\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  bottom=13mm,
  top=13mm
}

\pagestyle{empty}

\newcommand{\firstname}{Kenni Gandira}
\newcommand{\lastname}{Alamsyah}

\definecolor{blueSky}{RGB}{49, 120, 198}
\definecolor{orangeFruit}{RGB}{224, 128, 44}
\definecolor{redBlood}{RGB}{188, 20, 20}
\definecolor{grayShy}{RGB}{153, 150, 142}

\newcommand{\mainColor}{redBlood}

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

\newcommand{\xhspace}{\hspace*{0.1em}}
\newcommand{\shspace}{\hspace*{0.8em}}

\newcommand{\xvspace}{\vspace*{0.1em}}
\newcommand{\svspace}{\vspace*{0.5em}}

\begin{document}

\begin{center}
    {\Huge\textbf{\firstname{} \lastname}}\\[0.5em]
    {\large Senior Frontend Engineer}\\[1em]

    \texttt{devkenni.g@gmail.com} \textbar{} +62 81313635148 \textbar{} Bangkok, Thailand\\[0.5em]
    \texttt{linkedin.com/in/kenni-g-alamsyah}
\end{center}

\vspace{1.5em}

\noindent\today

\vspace{1em}

\noindent Dear Hiring Manager,

\vspace{0.5em}

I am writing to express my strong interest in the Senior Front End Developer role at IntelligenceBank. With 8+ years of experience specializing in React.js, Redux, and frontend development, I am excited about the opportunity to contribute to your mission of "Making Work Seem Less" through innovative marketing operations solutions.

\vspace{0.5em}

\textbf{Why IntelligenceBank resonates with me:}

Your commitment to making complex things simple and fostering innovation perfectly aligns with my professional philosophy. Having worked on design system implementation using Storybook that helped streamline development workflows, I understand the power of thoughtful solutions that reduce complexity while delivering exceptional user experiences. IntelligenceBank's focus on AI adoption and six-star service delivery particularly excites me, as I thrive in environments that push technological boundaries.

\vspace{0.5em}

\textbf{Relevant achievements that demonstrate my capability:}

At PropertyScout, I contributed to a web application revamp using React and modern JavaScript that resulted in a 27\% increase in user traffic. At AccelByte, I helped establish design system standards using Storybook and React, while contributing to developer experience improvements that achieved a 40\% reduction in compilation time. My performance optimization work includes improving Core Web Vitals metrics, specifically helping reduce Largest Contentful Paint from 4.5s to 1.2s at 99.co, while ensuring accessibility compliance across implementations.

\vspace{0.5em}

\textbf{Value I'll bring to IntelligenceBank:}

My expertise in complex React applications with Redux and Redux-saga directly addresses your technical requirements. Having collaborated with development teams and participated in code review processes, I'm prepared to contribute to your knowledge sharing culture and support team development efforts. My experience with modern frontend architecture, combined with my commitment to web accessibility standards and testing best practices, positions me to help drive your technical excellence initiatives while supporting your AI adoption goals.

\vspace{0.5em}

I am particularly drawn to IntelligenceBank's innovative approach to marketing operations and your emphasis on collaborative team culture. My background building scalable, performant applications for high-traffic platforms aligns well with your need for sophisticated frontend solutions that make work seem less burdensome for your clients.

\vspace{0.5em}

I would welcome the opportunity to discuss how my technical experience and passion for creating exceptional user experiences can contribute to IntelligenceBank's continued innovation and growth.

\vspace{0.5em}

Thank you for considering my application. I look forward to speaking with you about this exciting opportunity.

\vspace{1em}

Best regards,

\firstname{} \lastname

\end{document}