\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  top=25mm,
  bottom=25mm
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Kenni Gandira Alamsyah} \\
Bangkok, Thailand \\
+66 0842704245 \\
devkenni.g@gmail.com \\
\href{https://www.linkedin.com/in/kenni-g-alamsyah}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{1em}

\today

\vspace{1em}

\begin{flushleft}
Hiring Manager \\
Chubb \\
Bangkok, Thailand
\end{flushleft}

\vspace{1em}

Dear Hiring Manager,

\vspace{0.5em}

I am writing to express my strong interest in the Full Stack Engineer position at Chubb. With 8+ years of experience building scalable web applications across the entire technology stack, I am excited about the opportunity to contribute to Chubb's innovative Digital Claims solutions and help revolutionize claims handling in the digital era.

\vspace{0.5em}

Your focus on delivering cutting-edge Digital Claims solutions through the Chubb Studio platform strongly resonates with my passion for creating user-centric applications that solve real-world problems. I am particularly drawn to this role's emphasis on full-stack development using modern technologies like TypeScript and NodeJS to build robust applications that enhance client experiences during critical moments.

\vspace{0.5em}

Throughout my career, I have consistently delivered measurable impact through full-stack development:

\vspace{0.3em}

\begin{itemize}
    \item At PropertyScout, I developed end-to-end features using TypeScript, React, and Node.js, contributing to backend optimization, database design improvements, and query performance enhancements. I also contributed to a web application modernization initiative that drove a 27\% increase in user traffic (Q3).
    \item At AccelByte, I standardized developer experience across the engineering team, achieving a 40\% reduction in compilation time through strategic tooling improvements and build optimization.
    \item At 99.co, I achieved significant performance improvements, reducing Largest Contentful Paint from 4.5s to 1.2s (73\% improvement), directly enhancing user experience and engagement.
\end{itemize}

\vspace{0.5em}

My extensive experience with TypeScript, Node.js, and modern frontend frameworks (React, Vue.js, with transferable skills to Angular) positions me well to contribute immediately to your Digital Claims platform. I thrive in Agile environments and have proven success collaborating with cross-functional teams to deliver high-quality solutions. My problem-solving approach combines technical expertise with a focus on user experience, ensuring applications are both performant and intuitive.

\vspace{0.5em}

I am particularly excited about the opportunity to work on insurance technology that makes a tangible difference in people's lives during critical moments. I would welcome the chance to discuss how my background in building scalable, performant web applications can contribute to Chubb's continued innovation in digital claims.

\vspace{0.5em}

Thank you for considering my application. I look forward to speaking with you about this exciting opportunity.

\vspace{1em}

Best regards,

\vspace{1em}

Kenni Gandira Alamsyah

\end{document}
