\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}

\name{Kenni Gandira}{Alamsyah}
\phone[mobile]{+62~81313635148}
\email{devkenni.g@gmail.com}
\social[linkedin]{kenni-g-alamsyah}
\address{Bangkok, Thailand}{}{}

\begin{document}

\makecvtitle

\vspace{-30pt}

\section{}

Dear Hiring Manager,

\vspace{10pt}

I am writing to express my strong interest in the Middle Frontend Developer position at EveryMatrix. With 8+ years of experience building scalable React applications and a proven track record in performance optimization, I am excited about the opportunity to contribute to EveryMatrix's gaming platform development in Chiang Mai.

\vspace{8pt}

Your requirement for a React and Redux specialist resonates perfectly with my background. At PropertyScout, I contributed to a web application revamp that resulted in a 27\% increase in user traffic through performance improvements and modern React architecture. At AccelByte, I helped standardize the developer experience, achieving a 40\% reduction in compilation time while establishing component documentation standards using Storybook. Additionally, at 99.co, I improved Core Web Vitals by optimizing Largest Contentful Paint from 4.5s to 1.2s.

\vspace{8pt}

What draws me to EveryMatrix is your focus on code quality, scalability, and team collaboration---values that align with my professional approach. I have extensive experience maintaining high coding standards through regular code reviews, refactoring for improved scalability, and comprehensive documentation. My background includes working with React, Redux, REST APIs, and CI/CD workflows, which match your technical requirements precisely. I thrive in fast-paced environments and have demonstrated adaptability across gaming, real estate, and travel industries.

\vspace{8pt}

I am particularly excited about EveryMatrix's hybrid work model and commitment to professional development through learning platforms. Currently based in Bangkok, I am enthusiastic about relocating to Chiang Mai to join your team and contribute to building robust frontend solutions for AAA game developers.

\vspace{8pt}

I would welcome the opportunity to discuss how my experience in building performant, maintainable React applications can contribute to EveryMatrix's continued success.

\vspace{8pt}

Thank you for considering my application. I look forward to speaking with you about this exciting opportunity.

\vspace{10pt}

Best regards,

Kenni Gandira Alamsyah

\end{document}