%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+660842704245}{+66 0842704245} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah/}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
    \small{Senior Frontend Engineer with 8+ years of proven expertise architecting scalable, performant web applications across real estate, gaming, and travel industries. Specialized in React/TypeScript ecosystem, component-driven architecture, and performance optimization with measurable impact. Experienced in technical mentorship and driving engineering excellence through collaborative development and knowledge sharing.}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout (Real Estate Platform), Thailand}{2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Architected web application revamp driving \textbf{27\% increase in user traffic (Q3)} through strategic performance optimization, enhanced user experience, and modern frontend architecture.}
                \resumeItem{Modernized technology stacks with focus on performance and security, establishing scalable foundation for platform growth and long-term maintainability.}
                \resumeItem{Developed internal tools that enhanced operational productivity, streamlining development workflows and accelerating feature delivery across teams.}
                \resumeItem{Collaborated with UI/UX designers to translate complex design systems into pixel-perfect, responsive web elements with accessibility compliance.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{Accelbyte (Gaming Developer Tools), Indonesia}{2022 -- 2023}{}
            \resumeItemListStart
                \resumeItem{Engineered robust frontend tools and SDKs for AAA game developers, delivering production-grade solutions for complex gaming platforms.}
                \resumeItem{Improved developer experience, achieving \textbf{40\% reduction in compilation time} through strategic build optimization, Webpack configuration improvements, and tooling enhancements.}
                \resumeItem{Established component library and comprehensive styling documentation using \textbf{Storybook}, driving component reusability across teams and accelerating development velocity.}
                \resumeItem{Led knowledge-sharing initiatives and standardized code conventions across frontend team, elevating code quality and fostering collaborative engineering culture.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99 Group (Real Estate Platform), Bandung, Indonesia}{2020 -- 2022}{}
            \resumeItemListStart
                \resumeItem{Optimized site performance reducing \textbf{LCP from 4.5s to 1.2s} through comprehensive Core Web Vitals optimization, advanced performance profiling, and implementation of best practices.}
                \resumeItem{Increased organic site traffic through strategic SEO enhancements and schema validation implementation, directly impacting lead generation and user acquisition.}
                \resumeItem{Recognized with \textbf{"Own It" Quarterly Award Q2/21} for exceptional product ownership, technical excellence, and outstanding performance.}
                \resumeItem{Maintained industry-leading Core Web Vitals scores through continuous performance monitoring and proactive optimization.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com (Travel \& Hospitality), Jakarta, Indonesia}{2019 -- 2020}{}
            \resumeItemListStart
                \resumeItem{Implemented features using \textbf{React, TypeScript, Redux}, contributing to robust, type-safe frontend architecture.}
                \resumeItem{Maintained comprehensive component documentation using \textbf{Storybook}, ensuring design system consistency and accelerating developer onboarding.}
                \resumeItem{Drove regular refactoring initiatives for enhanced code scalability and maintainability, reducing technical debt and improving codebase health.}
                \resumeItem{Collaborated closely with product team to deliver UX enhancements, translating user needs into technical solutions.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency (now VML) (Marketing Agency), Bandung, Indonesia}{2018 -- 2019}{}
            \resumeItemListStart
                \resumeItem{Developed WordPress-based university platform (UPH) serving academic community with custom features and integrations.}
                \resumeItem{Developed customizable solutions for complex client requirements, demonstrating adaptability and technical problem-solving.}
                \resumeItem{Delivered full-stack solutions from backend to frontend, showcasing versatility across technology stack.}
            \resumeItemListEnd

        \resumeSubheading
            {Web Developer}{Hazani Rangka Utama (IT Services), Bandung, Indonesia}{2017 -- 2018}{}
            \resumeItemListStart
                \resumeItem{Developed three production WordPress themes for ThemeForest marketplace, adhering to strict quality standards and best practices.}
                \resumeItem{Ensured W3C validation and accessibility compliance across all projects, demonstrating commitment to web standards.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{PT NTCI (Education and Ecommerce), Yogyakarta, Indonesia}{2016 -- 2017}{}
            \resumeItemListStart
                \resumeItem{Launched career as software engineer, establishing strong foundation in web development principles and practices.}
                \resumeItem{Delivered multiple projects including e-learning platform and ticket booking applications with modern web technologies.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Proficient:} ReactJS, NextJS, React Native, VueJS, NuxtJS, Tailwind CSS, Redux, React Query, Javascript, Typescript, CSS, HTML
            \item \textbf{Familiar:} NodeJS, Electron, PHP, NestJS, ExpressJS, REST API, GraphQL, Strapi API, WordPress, Storybook, Cypress, React Testing Library, Jest, RabbitMQ, Redis
        }
    \resumeSubHeadingListEnd

%-----------LEADERSHIP & AWARDS-----------
\section{Leadership \& Awards}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{99 Group Hackathon} $|$ \emph{Best UI/UX Design Award}}{2021}
        \resumeProjectHeading
            {\textbf{Quarterly Award Q2/21} $|$ \emph{"Own It" Outstanding Performance}}{2021}
    \resumeSubHeadingListEnd

\end{document}
