%-------------------------
% Cover Letter in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{flushleft}
    \textbf{\Large Kenni Gandira Alamsyah} \\
    Bangkok, Thailand \\
    +66 0842704245 \\
    devkenni.g@gmail.com \\
    \href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{10pt}

\begin{flushleft}
    \today
\end{flushleft}

\vspace{10pt}

\begin{flushleft}
    Frontify Hiring Team \\
    Frontify AG \\
    Sankt Gallen, Switzerland
\end{flushleft}

\vspace{10pt}

Dear Hiring Manager,

I am excited to apply for the Senior Frontend Engineer - DAM position at Frontify. As a senior frontend engineer with 8+ years of proven expertise in React, TypeScript, and component-driven architecture, I am drawn to Frontify's mission to empower brands like Uber, Microsoft, and Volkswagen through innovative digital asset management solutions.

My experience demonstrates the value I can bring to your DAM team. At PropertyScout, I architected a web application revamp that drove a 27\% increase in user traffic through strategic performance optimization. At 99.co, I optimized site performance, reducing LCP from 4.5s to 1.2s through comprehensive Core Web Vitals optimization - this earned me the "Own It" Outstanding Performance award. These achievements reflect my ability to deliver measurable business impact through technical excellence.

Your requirements align closely with my expertise. I bring strong React and TypeScript experience across multiple production environments, having established component libraries using Storybook at AccelByte where I achieved a 40\% reduction in compilation time through build optimization. I have extensive API integration experience with both REST and GraphQL, and comprehensive testing knowledge with Jest, Cypress, and React Testing Library. Beyond technical skills, I actively mentor developers through code reviews, pair programming, and knowledge-sharing sessions - establishing engineering best practices and fostering collaborative culture.

The opportunity to work within Frontify's innovative engineering culture excites me. I thrive in collaborative environments where technical excellence and continuous improvement are valued. My experience migrating legacy code while architecting scalable solutions positions me to contribute meaningfully to your DAM platform's evolution from day one.

I would welcome the opportunity to discuss how my experience building performant, scalable frontend applications can contribute to Frontify's continued success in empowering brands worldwide.

Thank you for considering my application.

\vspace{10pt}

Best regards,

Kenni Gandira Alamsyah

\end{document}
