%-------------------------
% Cover Letter in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{flushleft}
    \textbf{\Large Kenni Gandira Alamsyah} \\
    Bangkok, Thailand \\
    +66 0842704245 \\
    devkenni.g@gmail.com \\
    \href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{10pt}

\begin{flushleft}
    \today
\end{flushleft}

\vspace{10pt}

\begin{flushleft}
    Frontify Hiring Team \\
    Frontify AG \\
    Sankt Gallen, Switzerland
\end{flushleft}

\vspace{10pt}

Dear Hiring Manager,

I am excited to apply for the Senior Frontend Engineer - DAM position at Frontify. With 8+ years of experience specializing in React, TypeScript, and component-driven architecture, I am drawn to Frontify's mission of empowering brands to turn ideas into impact through innovative digital asset management solutions.

Your platform's focus on helping teams like Uber, Microsoft, and Volkswagen organize digital assets and collaborate effectively resonates with my experience building scalable web applications. At PropertyScout, I contributed to a 27\% increase in user traffic through web application revamp and performance optimization. The challenge of evolving Frontify's DAM platform while maintaining scalability and developer experience aligns perfectly with my technical background.

My expertise directly matches your requirements. I have strong experience with React and TypeScript across multiple production environments, implemented component-driven architecture using Storybook at AccelByte (achieving 40\% reduction in compilation time), and have deep understanding of API integration including REST and GraphQL. At 99.co, I improved Core Web Vitals reducing LCP from 4.5s to 1.2s, demonstrating my commitment to performance optimization. I am experienced in mentoring developers, conducting code reviews, and fostering collaborative engineering culture through knowledge-sharing sessions.

The opportunity to work with a vibrant, collaborative team that values innovation and continuous improvement is particularly appealing. I thrive in environments where I can contribute to technical excellence while supporting team growth. My experience migrating legacy code and architecting maintainable solutions would add value to your DAM team's mission.

I would welcome the opportunity to discuss how my background in building performant, scalable frontend applications can contribute to Frontify's continued success.

Thank you for considering my application.

\vspace{10pt}

Best regards,

Kenni Gandira Alamsyah

\end{document}
