\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  bottom=13mm,
  top=13mm
}

\pagestyle{empty}

%%%%%%%%%%%%% Colors %%%%%%%%%%%%%

\definecolor{blueSky}{RGB}{49, 120, 198}
\definecolor{orangeFruit}{RGB}{224, 128, 44}
\definecolor{redBlood}{RGB}{188, 20, 20}
\definecolor{grayShy}{RGB}{153, 150, 142}

\newcommand{\mainColor}{redBlood} % pick a color above, or add a custom one

%%%%%%%%%%%%% Spaces %%%%%%%%%%%%%

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

% Horizontal %

\newcommand{\xhspace}{\hspace*{0.1em}}
\newcommand{\shspace}{\hspace*{0.8em}}

% Vertical %

\newcommand{\xvspace}{\vspace*{0.1em}}
\newcommand{\svspace}{\vspace*{0.5em}}
\newcommand{\mvspace}{\vspace*{1.5em}}
\newcommand{\hvspace}{\vspace*{2.5em}}

\newcommand{\negxvspace}{\vspace*{-0.2em}}
\newcommand{\negsvspace}{\vspace*{-0.5em}}
\newcommand{\negmvspace}{\vspace*{-1em}}
\newcommand{\neghvspace}{\vspace*{-1.5em}}

%%% Personal Details Macro %%%

\newcommand{\userInfo}[4]{
    \begin{flushleft}
        \color{\mainColor}
        \Huge
        \textbf{\MakeUppercase{ALAMSYAH}}
        \color{black}
        \textbf{Kenni Gandira}
        \color{\mainColor}
        \noindent\rule{19.1cm}{0.8pt}
        \color{grayShy}
        \small
        \par
        \parbox{7\spacebox} {
            \faMap \shspace #1 - #2 \par \svspace
            \faPhone \shspace #3 \par \svspace
            \faEnvelopeOpen \shspace \texttt{#4} \par \svspace
        }
        \color{\mainColor}
        \mvspace
    \end{flushleft}
    \negmvspace
}

%%% Company Details Macro %%%

\newcommand{\companyInfo}[4]{
    \begin{flushright}
        \parbox{4\spacebox}{
            \raggedleft
            \small
            \textbf{#1}\par
            \mvspace
            \color{grayShy} \textsc{\MakeLowercase{#2}}\par
            \xvspace
            \textsc{\MakeLowercase{#3}}\par
            \xvspace
            \textsc{\MakeLowercase{#4}}\par
            \color{black}
        }
    \end{flushright}
}

\begin{document}

\userInfo{Bangkok, Thailand}{SE Asia}{+62 81313635148}{devkenni.g@gmail.com}

\companyInfo{Zalando SE}{Hiring Manager}{Berlin, Germany}{Frontend Engineering Team}

\hvspace

Dear Hiring Manager,

I am writing to express my strong interest in the Senior Frontend Engineer position at Zalando SE. With 8+ years of experience building scalable web applications and a track record of contributing to meaningful performance improvements, I am excited about the opportunity to contribute to Zalando's mission of enhancing the customer experience for over 50 million fashion and lifestyle enthusiasts.

\textbf{Why I'm passionate about Zalando:}

As someone who has worked extensively in e-commerce platforms, I deeply appreciate Zalando's customer-centric approach and commitment to innovation in the fashion industry. Your focus on delivering exceptional user experiences through technology aligns perfectly with my career journey, where I've consistently prioritized performance optimization and user engagement. The opportunity to work with modern technologies like TypeScript, React, and GraphQL while contributing to Sports \& Beauty Propositions particularly excites me.

\textbf{How my experience aligns with your needs:}

At PropertyScout, I contributed to a web application revamp that resulted in a 27\% increase in user traffic, demonstrating my ability to create solutions that drive meaningful business impact. My work at AccelByte involved building high-performance React applications with TypeScript for gaming platforms, where I helped achieve a 40\% reduction in compilation time through developer experience improvements and standardization efforts. At 99.co, I contributed to Core Web Vitals performance optimization, reducing Largest Contentful Paint from 4.5s to 1.2s, directly enhancing user experience for property seekers across Southeast Asia.

\textbf{Value I'll bring to Zalando:}

My expertise in TypeScript, React/React Native, and NodeJS directly matches your technical requirements. Beyond technical skills, I bring a strong foundation in cross-functional collaboration, having worked closely with product managers, designers, and international teams. My experience supporting junior developers and participating in knowledge-sharing initiatives aligns with your need for someone who can contribute to team growth. Most importantly, my collaborative approach and focus on customer-centric solutions will help deliver the high-quality experiences that Zalando's users expect.

I am particularly drawn to Zalando's hybrid working model and culture of innovation. The opportunity to relocate to Berlin and contribute to a platform that impacts millions of users daily represents an exciting next step in my career.

Thank you for considering my application. I would welcome the opportunity to discuss how my background in building performant, scalable applications can contribute to Zalando's continued success.

\mvspace

Best regards,

Kenni Gandira Alamsyah

\end{document}