%-------------------------
% Cover Letter in LaTeX
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[11pt,a4paper]{letter}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[empty]{fullpage}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

\begin{flushleft}
\textbf{Kenni Gandira Alamsyah} \\
devkenni.g@gmail.com | +62 81313635148 \\
Bangkok, Thailand
\end{flushleft}

\vspace{1em}

Dear Hiring Manager,

I am writing to express my strong interest in the Front-End Software Engineer position at KAYAK. With 8+ years of experience building scalable web applications in React and TypeScript, including previous work at Tiket.com in the travel industry, I am excited about the opportunity to contribute to a platform that helps millions of travelers find the best deals.

My background aligns closely with KAYAK's needs. At PropertyScout, I contributed to web application improvements that resulted in a 27\% increase in user traffic. At 99.co, I worked on performance optimization that improved Largest Contentful Paint from 4.5s to 1.2s—work that directly translates to KAYAK's need for fast, responsive user experiences. At AccelByte, I helped standardize developer experience, contributing to a 40\% reduction in compilation time and establishing component styling and documentation using Storybook.

I have extensive experience with the technologies in your stack—React, TypeScript, CSS/SCSS, and comprehensive testing using Jest, Cypress, and React Testing Library. Having worked at Tiket.com, I understand the unique challenges of building travel platforms at scale and the importance of reliable, well-tested features.

I am particularly drawn to KAYAK's focus on end-to-end ownership and code quality, values that have driven my career. I am open to relocating to Berlin and excited about contributing to a product used by millions of travelers worldwide.

Thank you for considering my application. I look forward to discussing how my experience in performance optimization and scalable frontend architecture can contribute to KAYAK's continued success.

\vspace{1em}

Best regards,

Kenni Gandira Alamsyah

\end{document}