\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=20mm,
  right=20mm,
  bottom=20mm,
  top=20mm
}

\pagestyle{empty}

\begin{document}

% Header
\begin{flushleft}
    {\Huge\textbf{Kenni Gandira Alamsyah}}

    \vspace{0.3cm}

    {\small
    \faEnvelope\ devkenni.g@gmail.com \quad
    \faPhone\ +62 81313635148 \quad
    \faMapMarker\ Bangkok, Thailand

    \faLinkedin\ linkedin.com/in/kenni-g-alamsyah
    }
\end{flushleft}

\vspace{0.8cm}

\today

\vspace{0.5cm}

Dear Hiring Manager,

\vspace{0.3cm}

I am writing to express my strong interest in the Frontend Developer position at Maltem Asia-Pacific. With 8+ years of experience building scalable web applications using React, Vue.js, and mobile technologies, I am excited about the opportunity to contribute to your team's mission of transforming design visions into high-quality products.

\vspace{0.3cm}

\textbf{Why I'm a great fit:}

\vspace{0.2cm}

Your requirement for a proactive developer who challenges ideas to prevent inefficient solutions resonates deeply with my approach. At PropertyScout, I revamped web applications resulting in a 27\% increase in user traffic by collaborating closely with UI/UX designers and ensuring code quality through modern practices. My experience perfectly aligns with your need for someone who can transform designs into functional, user-friendly applications.

\vspace{0.3cm}

I bring strong expertise in both React and Vue.js frameworks, along with mobile development experience using React Native. At 99.co, I improved site performance by reducing LCP from 4.5s to 1.2s through Core Web Vitals optimization, demonstrating my commitment to quality and performance. I'm passionate about testing, having implemented comprehensive unit, integration, and automation tests using Jest, Cypress, and React Testing Library throughout my career.

\vspace{0.3cm}

Your emphasis on web security and accessibility aligns with my experience ensuring WCAG compliance and W3C validation across multiple projects. I thrive in Agile environments, having worked extensively with Jira while collaborating with backend developers, QA engineers, and product teams. Currently based in Bangkok, I'm immediately available and excited about the opportunity to work with a team that values technical excellence and continuous improvement.

\vspace{0.3cm}

I would welcome the opportunity to discuss how my background in building performant, accessible web applications can contribute to Maltem Asia-Pacific's continued success.

\vspace{0.3cm}

Thank you for considering my application. I look forward to speaking with you about this exciting opportunity.

\vspace{0.5cm}

Best regards,

\vspace{0.2cm}

Kenni Gandira Alamsyah

\end{document}