\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=20mm,
  right=20mm,
  bottom=20mm,
  top=20mm
}

\pagestyle{empty}

\begin{document}

% Header
\begin{flushleft}
    {\Huge\textbf{Kenni Gandira Alamsyah}}

    \vspace{0.3cm}

    {\small
    \faEnvelope\ devkenni.g@gmail.com \quad
    \faPhone\ +62 81313635148 \quad
    \faMapMarker\ Bangkok, Thailand

    \faLinkedin\ linkedin.com/in/kenni-g-alamsyah
    }
\end{flushleft}

\vspace{0.8cm}

\today

\vspace{0.5cm}

Dear Hiring Manager,

\vspace{0.3cm}

I am writing to express my interest in the Frontend Developer position at Maltem Asia-Pacific. With 8+ years of experience building web applications using React, Vue.js, and mobile technologies, I am excited about contributing to your team's mission of transforming design visions into high-quality products.

\vspace{0.3cm}

\textbf{Why I'm a strong match:}

\vspace{0.2cm}

Your requirement for a proactive developer who challenges ideas to prevent inefficient solutions resonates with my approach. At PropertyScout, I contributed to web application improvements that resulted in a 27\% increase in user traffic (Q3) while collaborating with UI/UX designers to transform designs into functional elements. This experience aligns well with your need for someone who can bridge design and development.

\vspace{0.3cm}

I have hands-on experience with both React and Vue.js frameworks, plus mobile development using React Native. At 99.co, I helped improve site performance by reducing LCP from 4.5s to 1.2s through Core Web Vitals optimization. I work with comprehensive testing approaches using Jest, Cypress, and React Testing Library to ensure code quality.

\vspace{0.3cm}

Your emphasis on web security and accessibility matches my experience with WCAG compliance and W3C validation across multiple projects. I thrive in Agile environments, having worked extensively with Jira while collaborating with backend developers, QA engineers, and product teams. Currently based in Bangkok, I'm immediately available and excited about working with a team that values technical excellence.

\vspace{0.3cm}

I would welcome the opportunity to discuss how my experience building performant, accessible web applications can contribute to Maltem Asia-Pacific's success.

\vspace{0.3cm}

Thank you for considering my application. I look forward to speaking with you about this opportunity.

\vspace{0.5cm}

Best regards,

\vspace{0.2cm}

Kenni Gandira Alamsyah

\end{document}