\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=20mm,
  right=20mm,
  bottom=20mm,
  top=20mm
}

\pagestyle{empty}

\begin{document}

% Header
\begin{center}
    {\LARGE\textbf{KENNI GANDIRA ALAMSYAH}}\\[0.3cm]
    Email: devkenni.g@gmail.com $|$ Phone: +62 81313635148 $|$ Location: Bangkok, Thailand\\
    LinkedIn: linkedin.com/in/kenni-g-alamsyah
\end{center}

\vspace{1cm}

% Date and Company Info
\today

\vspace{0.5cm}

Dear Hiring Manager,

\vspace{0.5cm}

I am writing to express my strong interest in the Frontend Engineer role. With 8+ years of experience as a Frontend Engineer specializing in React and TypeScript, I am excited about the opportunity to contribute to building exceptional web applications that deliver outstanding user experiences.

\vspace{0.3cm}

\textbf{Why I'm a great fit:}

\vspace{0.3cm}

My technical expertise aligns well with your requirements for modern frontend development. Throughout my career, I have focused on building scalable, performant applications using React.js and TypeScript. I am passionate about creating responsive, user-centric interfaces that prioritize both functionality and accessibility.

\vspace{0.3cm}

My contributions to team achievements include notable performance improvements:
\begin{itemize}
    \item At PropertyScout, I contributed to web application improvements that helped achieve a 27\% increase in user traffic
    \item At AccelByte, I helped standardize developer experience, contributing to a 40\% reduction in compilation time
    \item At 99.co, I worked with the team to improve site performance, helping reduce LCP from 4.5s to 1.2s through Core Web Vitals optimization
\end{itemize}

\vspace{0.3cm}

I bring strong collaboration skills, having worked closely with UI/UX designers, product managers, and backend engineers throughout my career. My experience with modern build tools (Webpack, Vite), comprehensive testing frameworks (Jest, Cypress, React Testing Library), and CSS frameworks (Tailwind CSS, SASS) ensures I can contribute immediately to your development workflow.

\vspace{0.3cm}

I am particularly excited about opportunities that involve performance optimization, team collaboration, and implementing best practices in React development. My experience mentoring junior developers and establishing coding standards would allow me to contribute not only to code quality but also to team growth and knowledge sharing.

\vspace{0.3cm}

I would welcome the opportunity to discuss how my background in building scalable, performant web applications can contribute to your team's success. Thank you for considering my application.

\vspace{0.5cm}

Best regards,\\
Kenni Gandira Alamsyah

\end{document}