\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{parskip}

\geometry{
  a4paper,
  left=20mm,
  right=20mm,
  bottom=20mm,
  top=20mm
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Kenni Gandira Alamsyah} \\
Bangkok, Thailand \\
+66 0842704245 \\
devkenni.g@gmail.com \\
linkedin.com/in/kenni-g-alamsyah
\end{flushleft}

\vspace{1em}

\begin{flushleft}
\today
\end{flushleft}

\vspace{1em}

\begin{flushleft}
Hiring Manager \\
Zscaler \\
Remote - USA
\end{flushleft}

\vspace{1em}

\textbf{RE: Senior Web Engineer Position}

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Senior Web Engineer position at Zscaler. With 8+ years building high-performance web applications using React, Node.js, and enterprise CMS platforms, I am energized by the opportunity to contribute to Zscaler's mission of enabling secure digital transformation for enterprises worldwide.

Zscaler's commitment to web engineering excellence and collaborative innovation aligns perfectly with my professional journey. I bring strong expertise in the core technologies for this role—React, Node.js, and PHP—combined with extensive CMS experience across WordPress (5+ years), Strapi, and OctoberCMS. My track record demonstrates rapid platform adaptability: I successfully executed a Vue 3 migration at AccelByte and implemented custom Strapi solutions at PropertyScout, showcasing my ability to quickly become productive with new enterprise CMS systems.

My web engineering achievements deliver measurable impact: I optimized Core Web Vitals reducing LCP from 4.5s to 1.2s, improved developer experience achieving 40\% compilation time reduction, and drove a 27\% increase in organic traffic through technical optimization and SEO implementation. At AccelByte, I collaborated across global teams spanning US, Singapore, and Poland time zones while implementing CI/CD pipelines with GitLab—directly applicable to Zscaler's distributed engineering culture.

I am particularly drawn to Zscaler's focus on web architecture best practices and automation frameworks. My experience building component libraries with Storybook, implementing accessibility standards, and optimizing build processes demonstrates the engineering discipline and scalable thinking required for this senior role.

I would welcome the opportunity to discuss how my background in building performant, accessible web applications can contribute to Zscaler's continued innovation and growth.

Thank you for considering my application. I look forward to exploring this exciting opportunity with your team.

\vspace{1em}

Best regards,

\vspace{2em}

Kenni Gandira Alamsyah

\end{document}
