\documentclass[11pt,a4paper]{letter}
\usepackage[sfdefault]{roboto}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\signature{Kenni Gandira Alamsyah}
\address{Bangkok, Thailand \\ devkenni.g@gmail.com \\ +62 813 1363 5148}

\begin{document}

\begin{letter}{Agoda Hiring Team \\ Bangkok, Thailand}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Software Engineer, Front End role at Agoda. As a Frontend Engineer with extensive React and TypeScript experience, I am excited about contributing to Agoda's mission of connecting travelers with accommodation worldwide.

\textbf{Why this role interests me:}

My experience at Tiket.com, one of Indonesia's online travel platforms, gave me valuable insights into the challenges of building travel technology interfaces. Agoda's global reach and diverse team of 95+ nationalities across 27 markets appeals to my interest in working within international, collaborative environments.

\textbf{Relevant experience:}

While I bring 8+ years of frontend development experience, I understand this is an entry-level position requiring 1-2 years. I am genuinely interested in this role because:
\begin{itemize}
    \item I am seeking opportunities to work with Agoda's specific technology stack and learn from your team
    \item The 6-month contract aligns with my current career goals
    \item I am open to contributing at the level required for this position
\end{itemize}

My recent work includes:
\begin{itemize}
    \item Contributing to a team effort that improved user traffic by 27\% at PropertyScout through React-based UI enhancements
    \item Working on the Tiket.com platform that serves Indonesian travelers
    \item Participating in performance optimization initiatives that improved Core Web Vitals metrics
\end{itemize}

\textbf{What I offer:}

I bring solid experience with React and TypeScript, familiarity with Git workflows, and proven ability to work in agile teams. My experience working with international colleagues has developed my English communication skills. Being already based in Bangkok, I am immediately available and familiar with the local market.

I understand this is a junior-level position and am prepared to work within the scope and compensation structure appropriate for this role. I am eager to learn from Agoda's engineering team and contribute to your frontend development efforts.

Thank you for considering my application. I look forward to discussing how I can contribute to Agoda's frontend team.

\closing{Best regards,}

\end{letter}

\end{document}