\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{tgpagella}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  bottom=13mm,
  top=13mm
}

\pagestyle{empty}

%%%%%%%%%%%% Change your first/lastname below %%%%%%%%%%%%

\newcommand{\firstname}{Kenni Gandira}
\newcommand{\lastname}{Alamsyah}

%%%%%%%%%%%%% Macros %%%%%%%%%%%%%

%%%%%%%%%%%%% Colors %%%%%%%%%%%%%

\definecolor{blueSky}{RGB}{49, 120, 198}
\definecolor{orangeFruit}{RGB}{224, 128, 44}
\definecolor{redBlood}{RGB}{188, 20, 20}
\definecolor{grayShy}{RGB}{153, 150, 142}

\newcommand{\mainColor}{redBlood} % pick a color above, or add a custom one

%%%%%%%%%%%%% Spaces %%%%%%%%%%%%%

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

% Horizontal %

\newcommand{\xhspace}{\hspace*{0.1em}}
\newcommand{\shspace}{\hspace*{0.8em}}

% Vertical %

\newcommand{\xvspace}{\vspace*{0.1em}}
\newcommand{\svspace}{\vspace*{0.5em}}
\newcommand{\mvspace}{\vspace*{1.5em}}
\newcommand{\hvspace}{\vspace*{2.5em}}

\newcommand{\negxvspace}{\vspace*{-0.2em}}
\newcommand{\negsvspace}{\vspace*{-0.5em}}
\newcommand{\negmvspace}{\vspace*{-1em}}
\newcommand{\neghvspace}{\vspace*{-1.5em}}

%%% Personal Details Macro %%%

\newcommand{\userInfo}[4]{
    \begin{flushleft}
        \color{\mainColor}
        \Huge
        \textbf{\MakeUppercase{\lastname}}
        \color{black}
        \textbf{\firstname}
        \color{\mainColor}
        \noindent\rule{19.1cm}{0.8pt}
        \color{grayShy}
        \small
        \par
        \parbox{7\spacebox} {
            \faMap \shspace #1 - #2 \par \svspace
            \faPhone \shspace #3 \par \svspace
            \faEnvelopeOpen \shspace \texttt{#4} \par \svspace
        }
        \color{\mainColor}
        \mvspace
    \end{flushleft}
    \negmvspace
}

%%% Company Details Macro %%%

\newcommand{\companyInfo}[4]{
    \begin{flushright}
        \parbox{4\spacebox}{
            \raggedleft
            \small
            \textbf{#1}\par
            \mvspace
            \color{grayShy} \textsc{\MakeLowercase{#2}}\par
            \xvspace
            \textsc{\MakeLowercase{#3}}\par
            \xvspace
            \textsc{\MakeLowercase{#4}}\par
            \color{black}
        }
    \end{flushright}
    \hvspace
}

%%% RE Macro %%%

\newcommand{\object}[1]{
    \small
    \color{\mainColor} \textbf{RE :} \color{black} \textbf{#1} \par
}

%%% Content Macro %%%

\newcommand{\content}[2]{
    \mvspace
    \begin{flushleft}
        \parbox{10.3\spacebox}{
          #1\par
          \svspace
          #2
        }\par
    \end{flushleft}
}

%%% Signature Macro %%%

\newcommand{\signature}{
    \svspace
    \parbox{3\spacebox}{
      Sincerely,\par
      \svspace \hspace{-0.3em}
      \textbf{\color{\mainColor} \MakeUppercase{\lastname} \color{black} \firstname}\par
      \svspace \svspace
      \Huge \faPenNib\par
    }\par
}

%%%%%%%%%%%% Your cover letter below %%%%%%%%%%%%

\begin{document}
\fontfamily{phv}\selectfont
\userInfo{Bangkok, Thailand}{}{+66 0842704245}{devkenni.g@gmail.com}
\companyInfo{College Board}{BigFuture Student Team}{Hiring Manager}{}
\object{Senior Full-Stack Engineer (UI Focus) Position}
\content{
  Dear Hiring Manager, \\

  I'm excited to apply for the Senior Full-Stack Engineer (UI Focus) position on College Board's BigFuture Student team. With 8+ years architecting React, TypeScript, and modern UI solutions, I'm energized by your mission of empowering 7 million students annually to discover their educational and career paths. \\

  At PropertyScout, I spearheaded a web application revamp that delivered a 27\% increase in user traffic through strategic performance optimizations and enhanced UX. At 99.co, I achieved a 73\% LCP improvement (4.5s→1.2s) through comprehensive Core Web Vitals optimization—directly boosting user engagement for thousands of daily visitors. These experiences reinforced how technical excellence creates measurable real-world impact. \\

  Your emphasis on mentorship and collaborative development resonates deeply. At AccelByte, I launched knowledge-sharing sessions and standardized code conventions, achieving a 40\% reduction in compilation time while fostering team growth and engineering excellence. I've consistently championed code reviews, comprehensive Storybook documentation, and frontend best practices throughout my career. \\

  My full-stack experience aligns closely with your needs. I bring strong proficiency in React, TypeScript, Next.js, and Node.js, with hands-on API development using GraphQL and Express.js. While my AWS Serverless experience is developing, I'm eager to deepen my expertise in Lambda, DynamoDB, and cloud-native architectures to build scalable solutions for millions of students. \\

  Most importantly, I developed the UPH university platform serving thousands of students, experiencing firsthand educational technology's transformative power. I'm excited to bring this passion, proven technical leadership, and full-stack expertise to help BigFuture continue empowering students nationwide to unlock their potential.\\
}{Thank you for considering my application.}
\signature
\end{document}
