\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=20mm,
  right=20mm,
  bottom=20mm,
  top=20mm
}

\pagestyle{empty}

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Kenni Gandira Alamsyah}}\\[0.3cm]
    devkenni.g@gmail.com $|$ +66 0842704245 $|$ linkedin.com/in/kenni-g-alamsyah\\[0.3cm]
    Bangkok, Thailand
\end{center}

\vspace{1cm}

% Date
\noindent
\today

\vspace{0.5cm}

% Recipient
\noindent
Hiring Manager\\
Synapses Thailand\\

\vspace{0.5cm}

% Subject
\noindent
\textbf{RE: Frontend Developer Position}

\vspace{0.5cm}

% Letter Content
\noindent
Dear Hiring Manager,

\vspace{0.3cm}

I am excited to apply for the Frontend Developer position at Synapses Thailand. With 8+ years of delivering high-impact React applications across real estate, gaming, and travel industries, I bring proven expertise in building intuitive, visually compelling user interfaces that drive measurable business results.

\vspace{0.3cm}

\noindent
\textbf{Why I'm an excellent fit:}

\vspace{0.3cm}

Your requirements align perfectly with my core strengths. At PropertyScout, I delivered a comprehensive application revamp that drove a 27\% increase in user traffic, working closely with UI/UX designers to transform Figma designs into polished, high-performance React components. My experience architecting backend APIs and optimizing frontend systems directly matches your needs for API integration expertise and performance-focused development.

\vspace{0.3cm}

My performance optimization track record demonstrates my commitment to exceptional user experiences. At 99.co, I achieved a 73\% improvement in load times by reducing LCP from 4.5s to 1.2s—work that earned me the company's "Own It" Quarterly Award. At AccelByte, I achieved a 40\% reduction in compilation time, significantly improving developer experience. These achievements reflect my ability to deliver the fast, reliable applications Synapses Thailand values.

\vspace{0.3cm}

I am particularly drawn to your focus on beautiful, user-friendly interfaces and the opportunity to work on mobile applications. My React Native experience and collaborative approach to design partnerships align perfectly with your emphasis on teamwork and continuous learning. I bring not just technical expertise, but a positive attitude, strong English communication skills, and genuine passion for creating exceptional digital experiences.

\vspace{0.3cm}

I would welcome the opportunity to discuss how my background in building scalable, performant web applications can contribute to Synapses Thailand's continued success and help deliver outstanding solutions for your clients.

\vspace{0.3cm}

Thank you for considering my application. I look forward to exploring this exciting opportunity with you.

\vspace{0.5cm}

\noindent
Best regards,

\vspace{0.3cm}

\noindent
Kenni Gandira Alamsyah

\end{document}
