%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+660842704245}{+66 0842704245} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah/}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
    \small{Frontend Engineer with 8+ years of experience building scalable web applications using React and modern JavaScript technologies. Delivered measurable business impact across real estate, gaming, and travel industries: improved LCP from 4.5s to 1.2s (73\% faster), achieved 40\% reduction in compilation time, and drove 27\% increase in user traffic through strategic application revamp. Award-winning developer recognized for technical excellence and product ownership, with expertise in performance optimization, API integration, and creating responsive, high-performance interfaces.}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout, Bangkok, Thailand}{2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Delivered comprehensive web application revamp, driving 27\% increase in user traffic (Q3) through enhanced performance and user experience.}
                \resumeItem{Transformed UI/UX design concepts into high-performance React components, working closely with designers to bridge design vision with technical implementation.}
                \resumeItem{Architected and integrated real-time backend APIs for property data and search functionality, ensuring seamless data flow and responsive user interactions.}
                \resumeItem{Modernized technology stack for optimal performance and security, future-proofing the application architecture.}
                \resumeItem{Enhanced internal tools that significantly improved operational productivity across the organization.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{AccelByte (Gaming Developer Tools), Remote}{2022 -- 2023}{}
            \resumeItemListStart
                \resumeItem{Developed sophisticated React-based tools and interfaces serving AAA game developers, directly impacting their development workflows.}
                \resumeItem{Achieved 40\% reduction in compilation time through strategic build optimization, saving significant development hours and improving developer experience.}
                \resumeItem{Established comprehensive component styling framework and documentation using Storybook, creating consistent UI patterns adopted across development teams.}
                \resumeItem{Led knowledge-sharing initiatives and standardized code conventions, elevating team-wide code quality and collaboration.}
                \resumeItem{Delivered developer-friendly interfaces through effective cross-functional collaboration with product and design teams.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99.co (Real Estate Platform), Bandung, Indonesia}{2020 -- 2022}{}
            \resumeItemListStart
                \resumeItem{Achieved 73\% improvement in load times by reducing Largest Contentful Paint (LCP) from 4.5s to 1.2s through advanced Core Web Vitals optimization.}
                \resumeItem{Architected and integrated backend APIs for property listing and search functionality, ensuring robust data handling and real-time updates.}
                \resumeItem{Enhanced site visibility and traffic through strategic SEO improvements and schema validation implementation.}
                \resumeItem{Maintained consistent Core Web Vitals optimization and high performance scores.}
                \resumeItem{Awarded "Own It" Quarterly Award Q2/21 for exceptional product ownership and technical excellence.}
                \resumeItem{Partnered with design team to implement intuitive, user-friendly interfaces that improved engagement.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com (Travel \& Hospitality), Jakarta, Indonesia}{2019 -- 2020}{}
            \resumeItemListStart
                \resumeItem{Implemented features using React, TypeScript, and Redux, building scalable state management for complex booking flows.}
                \resumeItem{Integrated comprehensive backend APIs for booking and payment functionality, ensuring secure and reliable transactions.}
                \resumeItem{Established component documentation with Storybook, facilitating team collaboration and accelerating development velocity.}
                \resumeItem{Executed strategic refactoring initiatives to improve code scalability and long-term maintainability.}
                \resumeItem{Coordinated with product team to deliver UX enhancements and feature improvements that elevated user satisfaction.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency (Marketing Agency), Bandung, Indonesia}{2018 -- 2019}{}
            \resumeItemListStart
                \resumeItem{Developed enterprise-scale WordPress-based university platform (UPH) with custom React components, serving thousands of students and faculty.}
                \resumeItem{Engineered customizable solutions for complex client requirements, balancing flexibility with maintainability.}
                \resumeItem{Built fully functional websites integrating backend and frontend technologies, delivering complete solutions from concept to deployment.}
                \resumeItem{Collaborated with design team to deliver responsive, user-friendly interfaces that exceeded client expectations.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Frontend Excellence:} React.js, Next.js, React Native, Redux.js, HTML5, CSS3, JavaScript, TypeScript, Tailwind CSS, SASS/SCSS, Styled Components, CSS-in-JS, Bootstrap
            \item \textbf{Full-Stack Capabilities:} Node.js, GraphQL, Express.js, RESTful APIs, Webpack, Gulp.js, Vite, npm, Jest, Cypress, React Testing Library, Storybook
            \item \textbf{Tools \& Version Control:} Git, GitHub, Bitbucket, Jira, Confluence, Figma
            \item \textbf{Additional Skills:} Core Web Vitals optimization, SEO implementation, Mobile development (React Native), Elasticsearch
        }
    \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS & RECOGNITION-----------
\section{Achievements \& Recognition}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Quarterly Award Q2/21 ("Own It")} $|$ \emph{99.co - Recognized for exceptional product ownership}}{2021}
        \resumeProjectHeading
            {\textbf{99 Group Hackathon - Best UI/UX Design Winner} $|$ \emph{Led award-winning design implementation}}{2021}
        \resumeProjectHeading
            {\textbf{Performance Impact:} \emph{LCP improvement from 4.5s to 1.2s (73\% faster load times)}}{}
        \resumeProjectHeading
            {\textbf{Developer Experience:} \emph{40\% reduction in compilation time, saving hours of development time}}{}
        \resumeProjectHeading
            {\textbf{Business Growth:} \emph{Drove 27\% increase in user traffic through strategic revamp}}{}
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{SMK Negeri 7 Bandung} $|$ \emph{Analytical Chemistry}}{2009 -- 2011}
    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
        \small{
            \item Web Development HTML CSS \& SEO Certification
            \item GDPR Certificate of Completion
            \item Anti-Harassment and Discrimination Certificate
        }
    \resumeSubHeadingListEnd

\end{document}
