\documentclass[11pt]{letter}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{
  a4paper,
  left=1in,
  right=1in,
  top=1in,
  bottom=1in
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\signature{Kenni Gandira Alamsyah \\ devkenni.g@gmail.com \\ +66 0842704245}
\address{Kenni Gandira Alamsyah \\ Bangkok, Thailand \\ devkenni.g@gmail.com \\ +66 0842704245}

\begin{document}

\begin{letter}{Hiring Manager \\ SumasEdge Corporation}

\opening{Dear Hiring Manager,}

I'm excited to apply for the Sr. React UI Developer position at SumasEdge Corporation. As a React specialist with 8+ years developing high-performance user interfaces, I bring proven expertise in React.js, Redux, modern JavaScript, and responsive design—backed by measurable results.

At PropertyScout, I developed a reusable React component library with Tailwind CSS that improved team efficiency by 40\% while ensuring pixel-perfect responsive design across all browsers. My experience spans the complete React ecosystem—from Redux state management to build tooling with Webpack and Vite.

\textbf{Key achievements:}
\begin{itemize}
    \item Achieved 73\% LCP improvement (4.5s → 1.2s) through Core Web Vitals optimization at 99.co
    \item Contributed to applications serving 500,000+ monthly users at PropertyScout and 165M+ users at Dana/Tiket.com
    \item Reduced compilation time by 40\% through Webpack optimization at AccelByte
    \item Consistently deliver cross-browser compatible experiences through rigorous testing
\end{itemize}

My remote work experience at AccelByte has prepared me for autonomous contribution while maintaining effective collaboration with distributed teams. I'm confident my React expertise and track record make me a strong fit for SumasEdge. I'd welcome the opportunity to discuss how I can contribute to your team's success.

Thank you for your consideration.

\closing{Best regards,}

\end{letter}

\end{document}
