\documentclass[11pt,a4paper]{letter}

\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

\signature{Kenni Gandira Alamsyah}
\address{
    Kenni Gandira Alamsyah \\
    Bangkok, Thailand \\
    \href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} \\
    +62 81313635148 \\
    \href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
}

\begin{document}

\begin{letter}{%
    Hiring Manager \\
    LoveCare Indonesia \\
    Jakarta, Indonesia
}

\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Front End Engineer role at LoveCare Indonesia. With 8+ years of experience specializing in React, Next.js, and TypeScript, I am excited about the opportunity to contribute to LoveCare's mission of delivering exceptional healthcare solutions through innovative technology.

\vspace{10pt}

Your emphasis on building responsive web applications with React, Next.js, and React Native particularly resonates with my technical background. At PropertyScout, I contributed to a web application revamp that resulted in a 27\% increase in user traffic through performance optimizations and enhanced user experiences. At AccelByte, I helped standardize developer workflows, achieving a 40\% reduction in compilation time. Most notably, at 99.co, I improved Core Web Vitals performance, reducing LCP from 4.5s to 1.2s through strategic optimization.

\vspace{10pt}

What draws me to LoveCare Indonesia is the opportunity to apply my technical expertise to the healthcare sector, where quality frontend development directly impacts user experience and accessibility. My experience with React Native positions me well to contribute to your mobile application development, while my proficiency in Jest and React Testing Library aligns with your focus on maintaining high-quality code. Additionally, as a winner of the 99 Group Hackathon for Best UI/UX Design, I bring a strong design sensibility that complements technical implementation.

\vspace{10pt}

I am particularly excited about joining a team that values code quality, performance optimization, and collaborative development. My experience conducting code reviews and contributing to best practices would enable me to support LoveCare's commitment to technical excellence.

\vspace{10pt}

I would welcome the opportunity to discuss how my background in building scalable, performant web applications can contribute to LoveCare Indonesia's continued growth and success.

\vspace{10pt}

Thank you for considering my application. I look forward to speaking with you about this exciting opportunity.

\closing{Best regards,}

\end{letter}

\end{document}