\documentclass[11pt,a4paper]{letter}

\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

\signature{Kenni Gandira Alamsyah}
\address{
    Kenni Gandira Alamsyah \\
    Bangkok, Thailand \\
    \href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} \\
    +62 81313635148 \\
    \href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
}

\begin{document}

\begin{letter}{%
    Hiring Manager \\
    LoveCare Indonesia \\
    Jakarta, Indonesia
}

\opening{Dear Hiring Manager,}

I am excited to apply for the Front End Engineer role at LoveCare Indonesia. With \textbf{8+ years of specialized experience} in React, Next.js, TypeScript, and React Native, I bring a proven track record of delivering measurable impact through technical excellence---and I'm eager to channel this expertise toward LoveCare's mission of transforming healthcare delivery through innovative technology.

\vspace{10pt}

Your requirements for building responsive web applications with React, Next.js, and React Native align perfectly with my core competencies. At PropertyScout, I \textbf{drove a 27\% increase in user traffic} through strategic web application modernization and performance optimization. At AccelByte, I \textbf{achieved a 40\% reduction in compilation time} by standardizing developer workflows for AAA game studios. Most notably, at 99.co, I \textbf{transformed Core Web Vitals performance---reducing LCP from 4.5s to 1.2s} (73\% improvement)---directly enhancing user experience and SEO rankings.

\vspace{10pt}

What excites me most about LoveCare Indonesia is the opportunity to apply my technical expertise where it matters most: improving healthcare accessibility and patient experience. My \textbf{React Native proficiency} positions me to contribute meaningfully to your mobile application development, while my expertise in \textbf{Jest and React Testing Library} ensures I'll uphold your commitment to code quality. As \textbf{winner of the 99 Group Hackathon for Best UI/UX Design}, I bring strong design sensibility that bridges the gap between beautiful interfaces and robust technical implementation---critical for healthcare applications where usability directly impacts patient outcomes.

\vspace{10pt}

I'm particularly drawn to joining a team that values performance optimization, accessibility standards, and collaborative development. My experience \textbf{conducting code reviews, establishing component libraries with Storybook, and leading knowledge-sharing initiatives} has prepared me to contribute to LoveCare's culture of technical excellence from day one. Additionally, my \textbf{GDPR certification and W3C accessibility compliance experience} demonstrate my commitment to security and inclusivity---essential considerations in healthcare technology.

\vspace{10pt}

I would be thrilled to discuss how my background in architecting scalable, performant web applications can accelerate LoveCare Indonesia's growth and enhance the healthcare experience for your users.

\vspace{10pt}

Thank you for considering my application. I look forward to the opportunity to contribute to your mission.

\closing{Best regards,}

\end{letter}

\end{document}