\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  bottom=13mm,
  top=13mm
}

\pagestyle{empty}

%%%%%%%%%%%% Change your first/lastname below %%%%%%%%%%%%

\newcommand{\firstname}{Kenni Gandira}
\newcommand{\lastname}{Alamsyah}

%%%%%%%%%%%%% Macros %%%%%%%%%%%%%

%%%%%%%%%%%%% Colors %%%%%%%%%%%%%

\definecolor{blueSky}{RGB}{49, 120, 198}
\definecolor{orangeFruit}{RGB}{224, 128, 44}
\definecolor{redBlood}{RGB}{188, 20, 20}
\definecolor{grayShy}{RGB}{153, 150, 142}

\newcommand{\mainColor}{redBlood} % pick a color above, or add a custom one

%%%%%%%%%%%%% Spaces %%%%%%%%%%%%%

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

% Horizontal %

\newcommand{\xhspace}{\hspace*{0.1em}}
\newcommand{\shspace}{\hspace*{0.8em}}

% Vertical %

\newcommand{\xvspace}{\vspace*{0.1em}}
\newcommand{\svspace}{\vspace*{0.5em}}
\newcommand{\mvspace}{\vspace*{1.5em}}
\newcommand{\hvspace}{\vspace*{2.5em}}

\newcommand{\negxvspace}{\vspace*{-0.2em}}
\newcommand{\negsvspace}{\vspace*{-0.5em}}
\newcommand{\negmvspace}{\vspace*{-1em}}
\newcommand{\neghvspace}{\vspace*{-1.5em}}

%%% Personal Details Macro %%%

\newcommand{\userInfo}[4]{
    \begin{flushleft}
        \color{\mainColor}
        \Huge
        \textbf{\MakeUppercase{\lastname}}
        \color{black}
        \textbf{\firstname}
        \color{\mainColor}
        \noindent\rule{19.1cm}{0.8pt}
        \color{grayShy}
        \small
        \par
        \parbox{7\spacebox} {
            \faMap \shspace #1 - #2 \par \svspace
            \faPhone \shspace #3 \par \svspace
            \faEnvelopeOpen \shspace \texttt{#4} \par \svspace
        }
        \color{\mainColor}
        \mvspace
    \end{flushleft}
    \negmvspace
}

%%% Company Details Macro %%%

\newcommand{\companyInfo}[4]{
    \begin{flushright}
        \parbox{4\spacebox}{
            \raggedleft
            \small
            \textbf{#1}\par
            \mvspace
            \color{grayShy} \textsc{\MakeLowercase{#2}}\par
            \xvspace
            \textsc{\MakeLowercase{#3}}\par
            \xvspace
            \textsc{\MakeLowercase{#4}}\par
            \color{black}
        }
    \end{flushright}
    \negmvspace
}

\begin{document}

\userInfo{Bangkok}{Thailand}{+62 81313635148}{devkenni.g@gmail.com}

\companyInfo{Pro Integrate}{Hiring Team}{Information Technology \& Product Development}{Squad Lead Position}

\mvspace

Dear Pro Integrate Hiring Team,

\svspace

I am writing to express my strong interest in the Squad Lead position at Pro Integrate. With 8+ years of experience as a Frontend Engineer and proven track record in team leadership and cross-functional collaboration, I am excited about the opportunity to lead a development squad at Pro Integrate's innovative eCommerce and digital ecosystem platform.

\svspace

\textbf{Why I'm a great fit:}

\svspace

Pro Integrate's focus on eCommerce technology and digital ecosystem development strongly resonates with my experience across diverse tech environments. Having worked in gaming (AccelByte), fintech (Bitkub), and real estate platforms, I understand the complexity of building scalable systems that serve thousands of users daily. Your emphasis on high code quality and collaborative development aligns perfectly with my approach to technical leadership.

\svspace

At AccelByte, I led knowledge-sharing initiatives across engineering teams and established component standardization that improved development efficiency by 40\%. At PropertyScout, I coordinated web application revamps resulting in 27\% increase in user traffic. These experiences demonstrate my ability to balance technical excellence with team development - essential qualities for a Squad Lead role.

\svspace

My approach to leadership centers on empowerment and collaborative problem-solving. I've mentored junior developers through structured code reviews, facilitated cross-team coordination with QA and DevOps teams, and created comprehensive technical documentation for team guidance. This matches your need for someone who can translate business requirements into actionable tasks while fostering a continuously improving team culture.

\svspace

I am particularly drawn to Pro Integrate because of your commitment to both technical innovation and team development. Your remote-first culture combined with focus on sprint deliverables and code quality standards creates an environment where I can leverage my experience in Agile ceremonies facilitation and performance monitoring to drive meaningful impact.

\svspace

I would welcome the opportunity to discuss how my background in leading technical initiatives and building collaborative team environments can contribute to Pro Integrate's continued success in the eCommerce technology space.

\svspace

Thank you for considering my application. I look forward to exploring this exciting opportunity with you.

\svspace

Best regards,

\svspace

Kenni Gandira Alamsyah

\end{document}