\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  bottom=13mm,
  top=13mm
}

\pagestyle{empty}

%%%%%%%%%%%% Change your first/lastname below %%%%%%%%%%%%

\newcommand{\firstname}{Kenni Gandira}
\newcommand{\lastname}{Alamsyah}

%%%%%%%%%%%%% Macros %%%%%%%%%%%%%

%%%%%%%%%%%%% Colors %%%%%%%%%%%%%

\definecolor{blueSky}{RGB}{49, 120, 198}
\definecolor{orangeFruit}{RGB}{224, 128, 44}
\definecolor{redBlood}{RGB}{188, 20, 20}
\definecolor{grayShy}{RGB}{153, 150, 142}

\newcommand{\mainColor}{redBlood} % pick a color above, or add a custom one

%%%%%%%%%%%%% Spaces %%%%%%%%%%%%%

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

% Horizontal %

\newcommand{\xhspace}{\hspace*{0.1em}}
\newcommand{\shspace}{\hspace*{0.8em}}

% Vertical %

\newcommand{\xvspace}{\vspace*{0.1em}}
\newcommand{\svspace}{\vspace*{0.5em}}
\newcommand{\mvspace}{\vspace*{1.5em}}
\newcommand{\hvspace}{\vspace*{2.5em}}

\newcommand{\negxvspace}{\vspace*{-0.2em}}
\newcommand{\negsvspace}{\vspace*{-0.5em}}
\newcommand{\negmvspace}{\vspace*{-1em}}
\newcommand{\neghvspace}{\vspace*{-1.5em}}

%%% Personal Details Macro %%%

\newcommand{\userInfo}[4]{
    \begin{flushleft}
        \color{\mainColor}
        \Huge
        \textbf{\MakeUppercase{\lastname}}
        \color{black}
        \textbf{\firstname}
        \color{\mainColor}
        \noindent\rule{19.1cm}{0.8pt}
        \color{grayShy}
        \small
        \par
        \parbox{7\spacebox} {
            \faMap \shspace #1 - #2 \par \svspace
            \faPhone \shspace #3 \par \svspace
            \faEnvelopeOpen \shspace \texttt{#4} \par \svspace
        }
        \color{\mainColor}
        \mvspace
    \end{flushleft}
    \negmvspace
}

%%% Company Details Macro %%%

\newcommand{\companyInfo}[4]{
    \begin{flushright}
        \parbox{4\spacebox}{
            \raggedleft
            \small
            \textbf{#1}\par
            \mvspace
            \color{grayShy} \textsc{\MakeLowercase{#2}}\par
            \xvspace
            \textsc{\MakeLowercase{#3}}\par
            \xvspace
            \textsc{\MakeLowercase{#4}}\par
            \color{black}
        }
    \end{flushright}
    \negmvspace
}

\begin{document}

\userInfo{Bangkok}{Thailand}{+62 81313635148}{devkenni.g@gmail.com}

\companyInfo{Pro Integrate}{Hiring Team}{Information Technology \& Product Development}{Squad Lead Position}

\mvspace

Dear Pro Integrate Hiring Team,

\svspace

I am writing to express my strong interest in the Squad Lead position at Pro Integrate. With 8+ years of experience as a Frontend Engineer and growing experience in team collaboration and technical mentorship, I am excited about the opportunity to transition into a leadership role within Pro Integrate's eCommerce and digital ecosystem platform.

\svspace

\textbf{Why I'm interested in this role:}

\svspace

Pro Integrate's focus on eCommerce technology and digital ecosystem development aligns well with my experience across diverse tech environments. Having worked in gaming (AccelByte) and real estate platforms, I understand the complexity of building scalable web applications. Your emphasis on high code quality and collaborative development matches my approach to software engineering and team contribution.

\svspace

At AccelByte, I initiated knowledge-sharing sessions and contributed to component standardization efforts that helped achieve a 40\% reduction in compilation time. At PropertyScout, I contributed to web application revamps that resulted in a 27\% increase in user traffic during Q3. These experiences have prepared me to take on greater responsibility in supporting team development and technical excellence.

\svspace

My approach to collaboration centers on knowledge sharing and supportive problem-solving. I have experience working closely with cross-functional teams including QA and UI/UX designers, and creating technical documentation to support team productivity. While I am seeking my first formal leadership role, I believe my collaborative experiences and technical expertise have prepared me to transition into the Squad Lead position.

\svspace

I am particularly drawn to Pro Integrate because of your commitment to both technical innovation and team development. Your remote-friendly culture combined with focus on sprint deliverables and code quality standards creates an environment where I can apply my technical experience while developing my leadership capabilities.

\svspace

I would welcome the opportunity to discuss how my background in technical collaboration and software development experience can contribute to Pro Integrate's continued success in the eCommerce technology space.

\svspace

Thank you for considering my application. I look forward to exploring this exciting opportunity with you.

\svspace

Best regards,

\svspace

Kenni Gandira Alamsyah

\end{document}