%-------------------------
% Cover Letter in Latex
% Author: Kenni Gandira Alamsyah
% Tailored for: FurtherAI - Frontend Engineer (Final Version)
%------------------------

\documentclass[11pt]{letter}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}

\signature{Kenni Gandira Alamsyah}
\address{
  Kenni Gandira Alamsyah \\
  Bangkok, Thailand \\
  \href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} \\
  +66 0842704245
}

\begin{document}

\begin{letter}{%
Hiring Manager \\
FurtherAI \\
San Francisco, CA
}

\opening{Dear Hiring Manager,}

I'm enthusiastic about applying for the Frontend Engineer - Web position at FurtherAI. With 8+ years of experience developing scalable web applications using React and TypeScript, I'm motivated by the opportunity to build AI-powered tools that transform how insurance professionals work.

Your mission to augment human expertise with AI aligns perfectly with my experience building enterprise SaaS products. At PropertyScout, I drove a 27\% increase in user traffic through strategic web application improvements. At AccelByte, I built developer tools for AAA game studios and achieved a 40\% reduction in compilation time while establishing our Storybook-based component library. At 99.co, I optimized Core Web Vitals, reducing LCP from 4.5s to 1.2s---a 73\% performance improvement.

My technical expertise directly matches FurtherAI's stack: React, TypeScript, Next.js, Tailwind CSS, and GraphQL. I've partnered with designers to transform Figma specs into production-ready features and built design systems using Storybook. I excel in cross-functional environments, working with design, product, and backend teams to ship features that balance usability, performance, and clean code.

What excites me most about FurtherAI is the challenge of building AI-powered workflows for a regulated industry. Turning complex insurance processes into simple, reliable interfaces is exactly the type of high-impact problem I excel at solving. My experience building data-intensive SaaS products, combined with my focus on performance and accessibility, positions me to contribute effectively to your product.

I'm eager to discuss how my background can support FurtherAI's mission to build the future of insurance operations.

\closing{Best regards,}

\end{letter}

\end{document}
