%-------------------------
% Cover Letter in Latex
% Author: Kenni Gandira Alamsyah
% Tailored for: FurtherAI - Frontend Engineer (Initial Draft)
%------------------------

\documentclass[11pt]{letter}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}

\signature{Kenni Gandira Alamsyah}
\address{
  Kenni Gandira Alamsyah \\
  Bangkok, Thailand \\
  \href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} \\
  +66 0842704245
}

\begin{document}

\begin{letter}{%
Hiring Manager \\
FurtherAI \\
San Francisco, CA
}

\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Frontend Engineer - Web position at FurtherAI. With 8+ years of experience building scalable web applications using React and TypeScript, I am excited about the opportunity to help build AI-powered tools that make insurance professionals more effective.

Your mission to augment human expertise with AI resonates deeply with my experience building enterprise SaaS products. At PropertyScout, I contributed to a 27\% increase in user traffic through web application improvements. At AccelByte, I built tools for AAA game developers and reduced compilation time by 40\% while establishing Storybook documentation for our component library. At 99.co, I improved Core Web Vitals, reducing LCP from 4.5s to 1.2s.

My technical background aligns closely with FurtherAI's stack. I have extensive experience with React, TypeScript, Next.js, Tailwind CSS, and GraphQL. I've collaborated with designers to translate Figma specs into production-ready features and contributed to design systems using Storybook. I thrive in cross-functional environments, working closely with design, product, and backend teams to ship features that balance usability, performance, and clean code.

I am particularly drawn to FurtherAI because of the opportunity to work on AI-powered workflows in a regulated industry. The challenge of turning complex insurance processes into simple, reliable interfaces excites me. I believe my experience building data-intensive SaaS products combined with my focus on performance and accessibility would enable me to contribute meaningfully to your product.

I would welcome the opportunity to discuss how my background can help FurtherAI build the future of insurance operations.

\closing{Best regards,}

\end{letter}

\end{document}
