%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
% Tailored for: FurtherAI - Frontend Engineer (Skeptical Version)
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+660842704245}{+66 0842704245} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
    \small{Frontend Engineer with 8+ years of experience building scalable web applications across real estate, gaming, and travel industries. Solid experience in React, TypeScript, and Next.js with a track record of contributing to design systems, performance optimization, and cross-functional product development. Contributed to measurable business results including 27\% user traffic growth, 40\% compilation time reduction, and 73\% performance improvement (LCP from 4.5s to 1.2s). Experienced in translating Figma designs into production-ready features and working with component libraries using Storybook.}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout, Bangkok, Thailand}{March 2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Contributed to web application revamp that resulted in 27\% increase in user traffic within Q3 through performance improvements and enhanced user experience.}
                \resumeItem{Collaborated with UI/UX designers to transform Figma designs into production-ready React and TypeScript components, ensuring accurate implementation and optimal user experience.}
                \resumeItem{Updated technology stacks across multiple web properties, improving performance, security, and maintainability for enhanced platform stability.}
                \resumeItem{Enhanced internal operational tools using modern frontend frameworks, contributing to improved team productivity and workflow efficiency.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{AccelByte, Remote}{June 2022 -- March 2023}{}
            \resumeItemListStart
                \resumeItem{Developed enterprise-grade tools and interfaces for AAA game developers building and scaling multiplayer games using React and TypeScript.}
                \resumeItem{Contributed to developer experience standardization initiative, helping achieve 40\% reduction in compilation time through build optimization and tooling improvements across the engineering team.}
                \resumeItem{Helped establish comprehensive component styling and documentation framework using Storybook, ensuring design system consistency and accelerating feature development.}
                \resumeItem{Initiated knowledge-sharing sessions and code convention standardization, contributing to improved frontend team capabilities and code quality.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99.co, Bandung, Indonesia}{July 2020 -- July 2022}{}
            \resumeItemListStart
                \resumeItem{Optimized site performance reducing LCP from 4.5s to 1.2s (73\% improvement) through Core Web Vitals optimization and strategic performance enhancements.}
                \resumeItem{Contributed to site traffic growth through SEO improvements and schema validation, enhancing search visibility and user acquisition.}
                \resumeItem{Recognized with "Own It" Quarterly Award Q2/21 for exceptional product ownership and initiative in delivering high-impact features.}
                \resumeItem{Maintained rigorous Core Web Vitals optimization and performance monitoring, ensuring consistent user experience excellence.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com, Jakarta, Indonesia}{August 2019 -- July 2020}{}
            \resumeItemListStart
                \resumeItem{Developed and shipped features for travel booking platform using React, TypeScript, and Redux, serving thousands of daily users.}
                \resumeItem{Built and maintained comprehensive component documentation with Storybook, enabling consistent UI development and faster onboarding.}
                \resumeItem{Conducted regular refactoring initiatives for improved code scalability, maintainability, and long-term technical health.}
                \resumeItem{Collaborated with product team to deliver UX enhancements and feature improvements that elevated user satisfaction.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency, Bandung, Indonesia}{July 2018 -- August 2019}{}
            \resumeItemListStart
                \resumeItem{Developed WordPress-based university platform (UPH) with custom functionality tailored to complex educational requirements.}
                \resumeItem{Created customizable solutions for intricate client requirements using PHP and JavaScript, delivering flexible and maintainable systems.}
                \resumeItem{Built fully functional websites spanning backend to frontend, demonstrating full-stack development capabilities.}
            \resumeItemListEnd

        \resumeSubheading
            {Web Developer}{Hazani Rangka Utama (Hartama), Bandung, Indonesia}{April 2017 -- August 2018}{}
            \resumeItemListStart
                \resumeItem{Developed and published three WordPress themes for ThemeForest marketplace, demonstrating commercial-grade development expertise.}
                \resumeItem{Ensured W3C validation and accessibility compliance, delivering inclusive and standards-compliant web experiences.}
            \resumeItemListEnd

        \resumeSubheading
            {Front End Developer}{PT NTCI, Yogyakarta, Indonesia}{March 2016 -- March 2017}{}
            \resumeItemListStart
                \resumeItem{Started career as software engineer, building multiple production applications including e-learning and ticket booking platforms.}
                \resumeItem{Contributed to team growth by interviewing and recruiting frontend developers, helping expand engineering capabilities.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Frontend:} React.js, React Native, Vue.js, Next.js, Redux.js, TypeScript, JavaScript, HTML5
            \item \textbf{Styling:} Tailwind CSS, CSS3, SASS/SCSS, Styled Components, CSS-in-JS, Bootstrap
            \item \textbf{Backend \& APIs:} Node.js, NestJS, GraphQL, Express.js
            \item \textbf{Build Tools:} Webpack, Vite, Gulp.js, npm
            \item \textbf{Testing \& Docs:} Jest, Cypress, React Testing Library, Storybook
            \item \textbf{Tools:} Git, GitHub, Bitbucket, Jira, Confluence, Figma, Elasticsearch
            \item \textbf{Performance:} Core Web Vitals optimization, SEO implementation
        }
    \resumeSubHeadingListEnd

%-----------KEY ACHIEVEMENTS-----------
\section{Key Achievements}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Performance \& Growth:} 27\% user traffic increase at PropertyScout, 40\% compilation time reduction at AccelByte, 73\% LCP improvement at 99.co}{}
        \resumeProjectHeading
            {\textbf{99 Group Hackathon} $|$ \emph{Best UI/UX Design Award}}{2021}
        \resumeProjectHeading
            {\textbf{Quarterly Award Q2/21} $|$ \emph{Exceptional Product Ownership}}{2021}
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{SMK Negeri 7 Bandung} $|$ \emph{Analytical Chemistry}}{2009 -- 2011}
    \resumeSubHeadingListEnd

\end{document}
