\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  bottom=25mm,
  top=25mm
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Kenni Gandira Alamsyah}\\
Bangkok, Thailand\\
+66 0842704245\\
devkenni.g@gmail.com\\
\href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{1em}

\begin{flushleft}
Hiring Manager\\
Bókun (Tripadvisor)\\
Reykjavík, Iceland
\end{flushleft}

\vspace{1em}

\textbf{RE: Front-end Software Engineer Position}

\vspace{1em}

Dear Hiring Manager,

I am writing to express my strong interest in the Front-end Software Engineer position at Bókun. With 8+ years of experience specializing in React and TypeScript, I am excited about the opportunity to help transform the tours and activities industry through innovative booking management solutions.

Your emphasis on creating user-friendly interfaces for tour operators resonates deeply with my experience building performant, intuitive applications. At PropertyScout, I revamped web applications that resulted in a 27\% increase in user traffic, demonstrating my ability to create solutions that genuinely improve user engagement. At AccelByte, I standardized developer experience and reduced compilation time by 40\%, showing my commitment to both user-facing excellence and developer productivity. Most notably, at 99.co, I improved Core Web Vitals by reducing LCP from 4.5s to 1.2s—critical work that directly translates to your need for responsive, high-performance booking interfaces.

My technical background aligns perfectly with Bókun's stack. I have extensive experience with TypeScript and React, complemented by expertise in Tailwind CSS and modern state management approaches. I've established component documentation using Storybook at multiple companies and regularly collaborate with designers and product managers to transform requirements into functional, elegant interfaces. My experience at Tiket.com—a travel booking platform—gives me valuable context for the unique challenges in the travel technology space.

I am particularly drawn to Bókun's mission of empowering tour operators with better technology. Beyond the professional opportunity, I must share that my wife and I have long dreamed of living in Iceland—its culture, natural beauty, and innovative spirit have always inspired us. The chance to combine this personal aspiration with meaningful work at Bókun, while contributing to the Tripadvisor ecosystem in a collaborative environment, feels like the perfect alignment of professional growth and life goals. I believe my combination of strong design sense, proven performance optimization skills, and passion for creating impactful user experiences would make me a valuable addition to your team.

I would welcome the opportunity to discuss how my background in building scalable, user-centric web applications can contribute to Bókun's continued growth.

Thank you for considering my application. I look forward to speaking with you about this opportunity.

\vspace{1em}

Best regards,

\textbf{Kenni Gandira Alamsyah}

\end{document}
