\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  bottom=25mm,
  top=25mm
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Kenni Gandira Alamsyah}\\
Bangkok, Thailand\\
+66 0842704245\\
devkenni.g@gmail.com\\
\href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{1em}

\begin{flushleft}
Hiring Manager\\
Bókun (Tripadvisor)\\
Reykjavík, Iceland
\end{flushleft}

\vspace{1em}

\textbf{RE: Front-end Software Engineer Position}

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Front-end Software Engineer position at Bókun, where I can contribute my 8+ years of specialized React and TypeScript expertise to transform the tours and activities industry through innovative booking management solutions.

Your emphasis on creating intuitive, user-friendly interfaces for tour operators resonates deeply with my proven track record. At PropertyScout, I led a web application revamp that drove a 27\% increase in user traffic, demonstrating my ability to create solutions that genuinely enhance user engagement and business results. At AccelByte, I standardized developer experience and achieved a 40\% compilation time reduction, showcasing my commitment to both exceptional user-facing experiences and engineering productivity. Most notably, at 99.co, I achieved a dramatic Core Web Vitals improvement—reducing LCP from 4.5s to 1.2s—the exact performance optimization expertise critical for delivering responsive, high-performance booking interfaces that delight users.

My technical foundation aligns perfectly with Bókun's modern stack. I bring extensive experience in TypeScript and React, complemented by hands-on expertise with Tailwind CSS, Next.js, and state management solutions. I've established comprehensive component documentation using Storybook at multiple companies and consistently collaborate with designers and product managers to transform complex requirements into elegant, functional interfaces. My frontend engineering experience at Tiket.com—a high-traffic travel booking platform—provides valuable context for the unique technical and user experience challenges in the travel technology space.

I am particularly drawn to Bókun's mission to empower tour operators with better technology. Beyond the professional opportunity, I'm inspired by Iceland's innovative culture, breathtaking natural beauty, and collaborative tech community. The opportunity to contribute meaningfully to Bókun's growth within the Tripadvisor ecosystem, while embracing Iceland's unique lifestyle, represents an ideal alignment of career advancement and personal aspirations. I am confident my proven performance optimization skills, strong design sensibility, and passion for creating impactful user experiences would make me a valuable contributor to your team.

I would welcome the opportunity to discuss how my background in building scalable, user-centric web applications can drive Bókun's continued success.

Thank you for considering my application. I look forward to speaking with you about this exciting opportunity.

\vspace{1em}

Best regards,

\textbf{Kenni Gandira Alamsyah}

\end{document}
