%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+660842704245}{+66 0842704245} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah/} $|$
    Bangkok, Thailand
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
    \small{Results-driven Frontend Engineer with 8+ years of proven expertise building intuitive, high-performance web applications using React and TypeScript. Demonstrated excellence in creating user-friendly interfaces that deliver measurable business results: 27\% traffic growth, dramatic performance improvements (LCP from 4.5s to 1.2s), and enhanced developer productivity. Strong design sensibility combined with technical depth, proven through Best UI/UX Design award and consistent delivery of elegant, scalable solutions across travel, real estate, and gaming industries.}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout, Thailand}{2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Led web application revamp that drove 27\% increase in user traffic (Q3) through modern React implementation and strategic UX optimization.}
                \resumeItem{Optimized Core Web Vitals, achieving exceptional 1.2-second page load times for seamless mobile and desktop user experiences.}
                \resumeItem{Transformed Figma designs into production-ready responsive components in collaboration with UI/UX design team.}
                \resumeItem{Integrated RESTful APIs powering real-time property listing platform with 17,000+ monthly updates.}
                \resumeItem{Enhanced internal development tools, measurably improving operational productivity and engineering efficiency.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{AccelByte, Remote}{2022 -- 2023}{}
            \resumeItemListStart
                \resumeItem{Developed enterprise-grade game developer dashboard using React and TypeScript, serving AAA game studios with intuitive interfaces.}
                \resumeItem{Achieved 40\% compilation time improvement (15 to 9 minutes) by optimizing Webpack configuration and streamlining developer experience.}
                \resumeItem{Established comprehensive component styling standards and Storybook documentation, ensuring design system consistency across product suite.}
                \resumeItem{Maximized frontend performance through strategic implementation of efficient data fetching patterns and intelligent asset optimization.}
                \resumeItem{Led knowledge-sharing initiatives to standardize code conventions, elevating team-wide development practices and code quality.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99.co, Bandung, Indonesia}{2020 -- 2022}{}
            \resumeItemListStart
                \resumeItem{Achieved Largest Contentful Paint (LCP) improvement from 4.5s to 1.2s through advanced Core Web Vitals optimization techniques and strategic performance tuning.}
                \resumeItem{Drove 25\% increase in user engagement through strategic performance enhancements and responsive design improvements.}
                \resumeItem{Increased organic traffic from 4,000 to 7,500 monthly visits (87\% growth) by implementing comprehensive SEO optimizations and schema validation.}
                \resumeItem{Improved frontend team velocity by 30\% through creation of reusable component library and comprehensive style guide.}
                \resumeItem{Recognized with "Own It" quarterly award for exceptional product ownership, technical leadership, and commitment to quality.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com, Jakarta, Indonesia}{2019 -- 2020}{}
            \resumeItemListStart
                \resumeItem{Led TypeScript migration initiative, establishing enterprise-level type safety across travel booking platform serving thousands of daily users.}
                \resumeItem{Developed critical booking and payment features using React, TypeScript, and Redux for high-traffic travel platform.}
                \resumeItem{Maintained comprehensive component documentation with Storybook, ensuring design consistency and enhanced developer productivity.}
                \resumeItem{Executed strategic code refactoring initiatives to improve long-term scalability, maintainability, and team efficiency.}
                \resumeItem{Partnered closely with product managers to enhance user experience based on data-driven customer insights and feedback.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency (now VML), Bandung, Indonesia}{2018 -- 2019}{}
            \resumeItemListStart
                \resumeItem{Developed WordPress-based platform for Pelita Harapan University (UPH), successfully serving 30,000+ students.}
                \resumeItem{Delivered responsive, cross-browser compatible solutions across multiple high-priority concurrent client projects.}
                \resumeItem{Built full-stack features seamlessly integrating frontend components with backend PHP services.}
                \resumeItem{Consistently achieved timely delivery and exceeded quality standards across diverse industry verticals.}
            \resumeItemListEnd

        \resumeSubheading
            {Web Developer}{Hazani Rangka Utama (Hartama), Bandung, Indonesia}{2017 -- 2018}{}
            \resumeItemListStart
                \resumeItem{Developed three commercial WordPress themes for ThemeForest marketplace, achieving 10,000+ total sales and positive user reviews.}
                \resumeItem{Ensured W3C validation and accessibility compliance across all projects, maintaining highest quality standards.}
                \resumeItem{Implemented responsive design patterns and comprehensive cross-browser compatibility for optimal user experience.}
                \resumeItem{Managed comprehensive customer support, delivering theme customizations and rapid issue resolution.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{PT NTCI, Yogyakarta, Indonesia}{2016 -- 2017}{}
            \resumeItemListStart
                \resumeItem{Built production e-learning and ticket booking applications using modern HTML5, CSS3, and JavaScript.}
                \resumeItem{Contributed to strategic team expansion from 3 to 15 members, supporting rapid company growth and development.}
                \resumeItem{Participated in establishing development standards and best practices, elevating overall code quality.}
                \resumeItem{Successfully balanced dual role as frontend developer and UI/UX designer across multiple concurrent projects.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Frontend Frameworks:} React.js, Next.js, React Native, Vue.js, Redux
            \item \textbf{Languages:} TypeScript, JavaScript, HTML5, CSS3, PHP
            \item \textbf{Styling:} Tailwind CSS, SASS/SCSS, Styled Components, CSS-in-JS, Bootstrap
            \item \textbf{Build Tools:} Webpack, Vite, npm, Gulp.js
            \item \textbf{Testing \& Documentation:} Jest, Cypress, React Testing Library, Storybook
            \item \textbf{Version Control:} Git, GitHub, Bitbucket
            \item \textbf{Backend Integration:} REST APIs, GraphQL, Node.js, Express.js
            \item \textbf{Performance:} Core Web Vitals optimization, SEO implementation
            \item \textbf{Design \& Collaboration:} Figma, Jira, Confluence
        }
    \resumeSubHeadingListEnd

%-----------LEADERSHIP & AWARDS-----------
\section{Leadership \& Awards}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{99 Group Hackathon} $|$ \emph{Best UI/UX Design Award}}{2021}
        \resumeProjectHeading
            {\textbf{Quarterly Award Q2/21} $|$ \emph{Outstanding Performance Recognition}}{2021}
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{SMK Negeri 7 Bandung} $|$ \emph{Analytical Chemistry}}{2009 -- 2011}
    \resumeSubHeadingListEnd

\end{document}
