\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\pagestyle{empty}

\begin{document}

% Header
\begin{flushleft}
\textbf{\Large Kenni Gandira Alamsyah}\\
Bangkok, Thailand\\
+66 0842704245 | devkenni.g@gmail.com\\
linkedin.com/in/kenni-g-alamsyah
\end{flushleft}

\vspace{1em}

October 5, 2025

\vspace{1em}

Dear Hiring Manager,

\vspace{1em}

I am writing to express my strong interest in the Senior Fullstack Developer (Front-End Focused) position at Lean Tech. With 8+ years of experience specializing in React, TypeScript, and performance optimization, I am excited about the opportunity to contribute to your mission of delivering exceptional nearshore solutions.

\vspace{1em}

Your focus on Core Web Vitals optimization resonates deeply with my experience. At 99.co, I reduced LCP from 4.5s to 1.2s (73\% improvement) while maintaining industry-leading FID and CLS metrics. This achievement, combined with my WordPress development experience at Mirum Agency, aligns perfectly with your WordPress-VIP content publishing workflow requirements.

\vspace{1em}

At PropertyScout, I architected frontend features using React and TypeScript while collaborating with cross-functional teams---exactly the collaborative approach Lean Tech values. My build tool optimization expertise (50\% build time reduction through Webpack configuration) and experience integrating REST APIs and GraphQL demonstrate the technical depth you're seeking.

\vspace{1em}

I am particularly drawn to Lean Tech's emphasis on mentorship and professional development. Throughout my career, I've conducted knowledge-sharing sessions, established coding standards, and mentored developers---contributing to team growth while maintaining high-quality code through automated testing and code reviews.

\vspace{1em}

As someone currently working remotely from Bangkok with experience collaborating across time zones, I'm well-prepared to contribute effectively to your distributed team and support your Latin American clients.

\vspace{1em}

I would welcome the opportunity to discuss how my performance optimization expertise and full-stack capabilities can contribute to Lean Tech's continued success.

\vspace{1em}

Thank you for considering my application.

\vspace{1em}

Best regards,\\
Kenni Gandira Alamsyah

\end{document}
