%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+6281313635148}{+62 81313635148} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
    \small{Frontend Engineer with 8+ years of experience specializing in React, TypeScript, and performance optimization. Proven expertise in Core Web Vitals optimization, WordPress development, and building scalable web applications. Track record of delivering measurable improvements including 27\% traffic increase, 40\% compilation time reduction, and 73\% LCP improvement.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Frontend:} React.js, TypeScript, JavaScript, Next.js, Vue.js, Redux.js, HTML5, CSS3
            \item \textbf{Styling:} Tailwind CSS, SASS/SCSS, Styled Components, CSS-in-JS, Bootstrap
            \item \textbf{Backend:} Node.js, NestJS, Express.js, GraphQL, REST APIs
            \item \textbf{Build Tools:} Webpack, Vite, Gulp.js, npm
            \item \textbf{Testing:} Jest, Cypress, React Testing Library, Storybook
            \item \textbf{CMS:} WordPress, Strapi.js, OctoberCMS
            \item \textbf{Performance:} Core Web Vitals optimization, SEO implementation
            \item \textbf{Tools:} Git, GitHub, Bitbucket, Jira, Confluence, Figma, Elasticsearch
        }
    \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout (Real Estate Platform), Thailand}{2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Revamped web applications using React and TypeScript, resulting in 27\% increase in user traffic (Q3).}
                \resumeItem{Collaborated with UI/UX designers to transform designs into functional web elements.}
                \resumeItem{Updated technology stacks for optimal performance and security.}
                \resumeItem{Improved internal tools for enhanced operational productivity.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{Accelbyte (Gaming Developer Tools), Indonesia}{2022 -- 2023}{}
            \resumeItemListStart
                \resumeItem{Developed developer tools for AAA game developers using React and TypeScript.}
                \resumeItem{Standardized developer experience achieving 40\% reduction in compilation time through build tool optimization.}
                \resumeItem{Established component styling and documentation using Storybook.}
                \resumeItem{Initiated knowledge-sharing sessions and code convention standardization.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99 Group (Real Estate Platform), Bandung, Indonesia}{2020 -- 2022}{}
            \resumeItemListStart
                \resumeItem{Improved site performance reducing LCP from 4.5s to 1.2s (73\% improvement) through Core Web Vitals optimization.}
                \resumeItem{Enhanced site traffic through SEO improvements and schema validation.}
                \resumeItem{Maintained Core Web Vitals optimization across the platform.}
                \resumeItem{Received "Own It" award for product ownership.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com (Travel \& Hospitality), Jakarta, Indonesia}{2019 -- 2020}{}
            \resumeItemListStart
                \resumeItem{Implemented features using React, TypeScript, and Redux.}
                \resumeItem{Maintained component documentation with Storybook.}
                \resumeItem{Conducted regular refactoring for code scalability.}
                \resumeItem{Coordinated with product team for UX enhancements.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency (now VML) (Marketing Agency), Bandung, Indonesia}{2018 -- 2019}{}
            \resumeItemListStart
                \resumeItem{Developed WordPress-based university platform (UPH).}
                \resumeItem{Created customizable solutions for complex requirements.}
                \resumeItem{Built fully functional websites from backend to frontend.}
            \resumeItemListEnd

        \resumeSubheading
            {Web Developer}{Hazani Rangka Utama (IT Services), Bandung, Indonesia}{2017 -- 2018}{}
            \resumeItemListStart
                \resumeItem{Developed three WordPress themes for ThemeForest.}
                \resumeItem{Handled W3C validation and accessibility compliance.}
                \resumeItem{Managed customer support and product iterations.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{PT NTCI (Education and Ecommerce), Yogyakarta, Indonesia}{2016 -- 2017}{}
            \resumeItemListStart
                \resumeItem{Built multiple projects including e-learning and ticket booking applications.}
                \resumeItem{Interviewed and recruited frontend developers.}
                \resumeItem{Took on dual role as frontend developer and UI/UX designer.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------KEY ACHIEVEMENTS-----------
\section{Key Achievements}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{27\% increase in user traffic (Q3)} $|$ \emph{PropertyScout}}{2023}
        \resumeProjectHeading
            {\textbf{40\% reduction in compilation time} $|$ \emph{AccelByte}}{2022}
        \resumeProjectHeading
            {\textbf{LCP improvement from 4.5s to 1.2s (73\%)} $|$ \emph{99.co}}{2021}
        \resumeProjectHeading
            {\textbf{Quarterly Award Q2/21} $|$ \emph{99 Group}}{2021}
        \resumeProjectHeading
            {\textbf{99 Group Hackathon - Best UI/UX Design}}{2021}
    \resumeSubHeadingListEnd

\end{document}
