\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\pagestyle{empty}

\begin{document}

% Header
\begin{flushleft}
\textbf{\Large Kenni Gandira Alamsyah}\\
Bangkok, Thailand\\
+66 0842704245 | devkenni.g@gmail.com\\
linkedin.com/in/kenni-g-alamsyah
\end{flushleft}

\vspace{1em}

October 5, 2025

\vspace{1em}

Dear Hiring Manager,

\vspace{1em}

I am excited to apply for the Senior Fullstack Developer (Front-End Focused) position at Lean Tech. With 8+ years of experience architecting high-performance web applications and a proven track record of delivering measurable business impact, I am enthusiastic about contributing to your mission of delivering exceptional nearshore solutions to clients worldwide.

\vspace{1em}

Your emphasis on Core Web Vitals optimization resonates strongly with my expertise and passion for performance engineering. At 99.co, I transformed site performance by reducing Largest Contentful Paint from 4.5s to 1.2s---a 73\% improvement that drove significant organic traffic growth while maintaining industry-leading FID and CLS metrics. Combined with my WordPress development experience at Mirum Agency (custom university platform) and Hazani Rangka Utama (ThemeForest theme development), I bring directly relevant expertise for your WordPress-VIP content publishing workflow requirements.

\vspace{1em}

At PropertyScout, I architected frontend features using React and TypeScript that drove 27\% traffic growth (Q3), while collaborating closely with cross-functional teams---exactly the collaborative, results-driven approach Lean Tech values. My build tool optimization expertise (40\% compilation time reduction through strategic Webpack configuration at AccelByte) and extensive experience integrating REST APIs and GraphQL demonstrate the technical depth and full-stack capabilities you're seeking.

\vspace{1em}

I am particularly drawn to Lean Tech's commitment to mentorship and professional development. Throughout my career, I've been passionate about elevating team capabilities---conducting knowledge-sharing sessions at AccelByte, establishing coding standards and best practices, and mentoring developers to grow their skills. I believe in building not just great products, but great teams, and I'm excited about contributing to Lean Tech's collaborative culture.

\vspace{1em}

As someone currently thriving in remote work from Bangkok with proven experience collaborating across time zones and distributed teams, I'm well-positioned to contribute effectively to your team and deliver exceptional value to your Latin American clients from day one.

\vspace{1em}

I would welcome the opportunity to discuss how my performance optimization expertise, full-stack capabilities, and collaborative mindset can contribute to Lean Tech's continued growth and success.

\vspace{1em}

Thank you for considering my application.

\vspace{1em}

Best regards,\\
Kenni Gandira Alamsyah

\end{document}
