%-------------------------
% Cover Letter in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{#2}}}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{flushleft}
    {\Large \textbf{Kenni Gandira Alamsyah}} \\
    \vspace{4pt}
    \link{https://api.whatsapp.com/send/?phone=+660842704245}{+66 0842704245} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{10pt}

%----------DATE----------
\today

\vspace{10pt}

%----------RECIPIENT----------
Dear Hiring Manager,

%----------BODY----------
I am writing to express my strong interest in the Senior Software Engineer (ReactJS) position at Hubble.Build. With 8+ years of experience building scalable web applications using React and TypeScript, I am excited about the opportunity to contribute to revolutionizing the construction industry through innovative technology solutions.

Hubble's mission to build autonomous construction sites through digitized workflows resonates deeply with my experience optimizing complex systems. At PropertyScout, I led a web application revamp that increased user traffic by 27\% while reducing page load time to 1.2 seconds through Core Web Vitals optimization. This experience taught me the importance of creating efficient, user-centric platforms that connect stakeholders effectively—principles that align perfectly with Hubble's vision.

Your requirements for ReactJS expertise, TypeScript proficiency, and build tool optimization match my core strengths. At AccelByte, I achieved a 40\% reduction in compilation time by optimizing Webpack configurations and standardizing development processes. I have consistently led frontend architecture decisions, established component libraries, and mentored engineering teams across real estate, gaming, and travel industries.

I am particularly drawn to Hubble because of the opportunity to apply my technical expertise to transform the construction industry. My track record of adapting to new domains—from real estate to gaming—demonstrates my ability to quickly understand complex business requirements and deliver impactful solutions.

I would welcome the opportunity to discuss how my experience building high-performance React applications and leading frontend initiatives can contribute to Hubble's continued innovation.

Thank you for considering my application. I look forward to speaking with you about this exciting opportunity.

%----------CLOSING----------
\vspace{10pt}

Best regards,

Kenni Gandira Alamsyah

\end{document}