%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+660842704245}{+66 0842704245} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah/}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
    \small{Senior Frontend Engineer with 8+ years of experience specializing in ReactJS, TypeScript, and modern web application development. Proven track record of building scalable, performant web solutions and leading frontend architecture decisions across real estate, gaming, and travel industries. Expert in optimizing build processes, establishing frontend standards, and mentoring engineering teams.}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout (Real Estate Platform), Bangkok, Thailand}{2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Revamped web applications using React and TypeScript, resulting in 27\% increase in user traffic (Q3 2024).}
                \resumeItem{Led Core Web Vitals optimization initiatives, reducing page load time to 1.2 seconds and boosting monthly page visits by 44\% in 4 months.}
                \resumeItem{Collaborated with UI/UX designers to transform Figma designs into production-ready React components.}
                \resumeItem{Updated technology stacks and internal tools for enhanced performance, security, and operational productivity.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{AccelByte (Gaming Developer Tools), Remote}{2022 -- 2023}{}
            \resumeItemListStart
                \resumeItem{Developed and maintained React-based web applications for AAA game developers.}
                \resumeItem{Achieved 40\% reduction in compilation time (15 to 9 minutes) by optimizing Webpack configurations and standardizing development processes.}
                \resumeItem{Established component styling system and comprehensive documentation using Storybook.}
                \resumeItem{Initiated knowledge-sharing sessions focusing on React best practices and frontend architecture patterns.}
                \resumeItem{Led code convention standardization across frontend teams.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99.co (Real Estate Platform), Bandung, Indonesia}{2020 -- 2022}{}
            \resumeItemListStart
                \resumeItem{Optimized Core Web Vitals performance, reducing Largest Contentful Paint (LCP) from 4.5s to 1.2s.}
                \resumeItem{Increased frontend team productivity by 30\% through implementing style guide and component library.}
                \resumeItem{Enhanced site's SEO architecture, growing organic traffic from 4,000 to 7,500 monthly visits (87\% increase).}
                \resumeItem{Received "Own It" Quarterly Award Q2/21 for exceptional product ownership and technical excellence.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com (Travel \& Hospitality), Jakarta, Indonesia}{2019 -- 2020}{}
            \resumeItemListStart
                \resumeItem{Led TypeScript migration initiative from scratch, establishing type safety standards and development patterns.}
                \resumeItem{Implemented features using React, TypeScript, and Redux for scalable travel booking platform.}
                \resumeItem{Maintained comprehensive component documentation with Storybook for improved developer experience.}
                \resumeItem{Coordinated with product team to deliver UX enhancements aligned with user needs.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency (Marketing Agency), Bandung, Indonesia}{2018 -- 2019}{}
            \resumeItemListStart
                \resumeItem{Managed multiple concurrent client projects with React and modern JavaScript frameworks.}
                \resumeItem{Developed official website for Universitas Pelita Harapan (UPH) using WordPress and custom React components.}
                \resumeItem{Created customizable frontend solutions for complex client requirements across diverse industries.}
            \resumeItemListEnd

        \resumeSubheading
            {Web Developer}{Hazani Rangka Utama (IT Services), Bandung, Indonesia}{2017 -- 2018}{}
            \resumeItemListStart
                \resumeItem{Designed and developed custom WordPress themes with modern JavaScript enhancements.}
                \resumeItem{Handled W3C validation and accessibility compliance for all web projects.}
                \resumeItem{Managed customer support and product iterations based on user feedback.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{PT NTCI (Education \& E-commerce), Yogyakarta, Indonesia}{2016 -- 2017}{}
            \resumeItemListStart
                \resumeItem{Built multiple projects including e-learning and ticket booking applications using React and modern JavaScript.}
                \resumeItem{Participated in expanding development team from 3 to 15 members.}
                \resumeItem{Contributed to establishing frontend development standards and best practices.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Frontend Frameworks \& Libraries:} ReactJS, React Native, NextJS, VueJS, NuxtJS, Redux, React Query, Electron
            \item \textbf{Languages:} JavaScript (ES6+), TypeScript, HTML5, CSS3, PHP
            \item \textbf{Styling \& CSS:} Tailwind CSS, Styled Components, CSS-in-JS, SASS/SCSS, Bootstrap
            \item \textbf{Build Tools \& DevOps:} Webpack, Vite, Gulp, npm, CI/CD pipelines
            \item \textbf{Backend \& APIs:} NodeJS, NestJS, ExpressJS, REST API, GraphQL
            \item \textbf{Testing \& Documentation:} Jest, Cypress, React Testing Library, Storybook
            \item \textbf{Version Control:} Git, GitHub, Bitbucket
            \item \textbf{Additional:} Core Web Vitals optimization, SEO, Figma, Jira, Confluence
        }
    \resumeSubHeadingListEnd

%-----------LEADERSHIP & AWARDS-----------
\section{Leadership \& Awards}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{99 Group Hackathon} $|$ \emph{Best UI/UX Design Award}}{2021}
        \resumeProjectHeading
            {\textbf{Quarterly Award Q2/21} $|$ \emph{Outstanding Performance}}{2021}
    \resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{Languages}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{English:} Professional proficiency
            \item \textbf{Bahasa Indonesia:} Native
            \item \textbf{Sundanese:} Native
        }
    \resumeSubHeadingListEnd

\end{document}