%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+660842704245}{+66 0842704245} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah/}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
    \small{Senior Frontend Engineer with 8+ years of experience specializing in ReactJS, TypeScript, and modern web application development. Proven track record of building scalable, performant web solutions and contributing to frontend architecture decisions across real estate, gaming, and travel industries. Experienced in optimizing build processes, establishing frontend standards, and mentoring engineering teams.}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout (Real Estate Platform), Bangkok, Thailand}{2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Contributed to web application revamp using React and TypeScript, resulting in 27\% increase in user traffic (Q3 2024).}
                \resumeItem{Updated technology stacks and internal tools for enhanced performance, security, and operational productivity.}
                \resumeItem{Collaborated with UI/UX designers to transform Figma designs into production-ready React components.}
                \resumeItem{Improved internal tools for enhanced operational productivity.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{AccelByte (Gaming Developer Tools), Remote}{2022 -- 2023}{}
            \resumeItemListStart
                \resumeItem{Developed and maintained React-based web applications for AAA game developers.}
                \resumeItem{Contributed to standardizing developer experience, achieving 40\% reduction in compilation time (15 to 9 minutes) through optimized Webpack configurations.}
                \resumeItem{Established component styling system and comprehensive documentation using Storybook.}
                \resumeItem{Initiated knowledge-sharing sessions focusing on React best practices and frontend architecture patterns.}
                \resumeItem{Contributed to code convention standardization across frontend teams.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99.co (Real Estate Platform), Bandung, Indonesia}{2020 -- 2022}{}
            \resumeItemListStart
                \resumeItem{Optimized Core Web Vitals performance, reducing Largest Contentful Paint (LCP) from 4.5s to 1.2s.}
                \resumeItem{Enhanced site's SEO architecture, improving organic traffic through schema validation and technical SEO improvements.}
                \resumeItem{Maintained Core Web Vitals optimization and performance monitoring.}
                \resumeItem{Received "Own It" Quarterly Award Q2/21 for exceptional product ownership and technical excellence.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com (Travel \& Hospitality), Jakarta, Indonesia}{2019 -- 2020}{}
            \resumeItemListStart
                \resumeItem{Implemented features using React, TypeScript, and Redux for scalable travel booking platform.}
                \resumeItem{Maintained comprehensive component documentation with Storybook for improved developer experience.}
                \resumeItem{Conducted regular refactoring for code scalability and maintainability.}
                \resumeItem{Coordinated with product team to deliver UX enhancements aligned with user needs.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency (Marketing Agency), Bandung, Indonesia}{2018 -- 2019}{}
            \resumeItemListStart
                \resumeItem{Managed multiple concurrent client projects with React and modern JavaScript frameworks.}
                \resumeItem{Developed official website for Universitas Pelita Harapan (UPH) using WordPress and custom components.}
                \resumeItem{Created customizable frontend solutions for complex client requirements across diverse industries.}
            \resumeItemListEnd

        \resumeSubheading
            {Web Developer}{Hazani Rangka Utama (IT Services), Bandung, Indonesia}{2017 -- 2018}{}
            \resumeItemListStart
                \resumeItem{Developed three WordPress themes with modern JavaScript enhancements.}
                \resumeItem{Handled W3C validation and accessibility compliance for all web projects.}
                \resumeItem{Managed customer support and product iterations based on user feedback.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{PT NTCI (Education \& E-commerce), Yogyakarta, Indonesia}{2016 -- 2017}{}
            \resumeItemListStart
                \resumeItem{Built multiple projects including e-learning and ticket booking applications using modern JavaScript.}
                \resumeItem{Interviewed and recruited frontend developers to support team growth.}
                \resumeItem{Contributed to establishing frontend development standards and best practices.}
                \resumeItem{Took on dual role as frontend developer and UI/UX designer.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Frontend Frameworks \& Libraries:} ReactJS, React Native, NextJS, VueJS, Redux, Electron
            \item \textbf{Languages:} JavaScript (ES6+), TypeScript, HTML5, CSS3, PHP
            \item \textbf{Styling \& CSS:} Tailwind CSS, Styled Components, CSS-in-JS, SASS/SCSS, Bootstrap
            \item \textbf{Build Tools \& DevOps:} Webpack, Vite, Gulp, npm
            \item \textbf{Backend \& APIs:} NodeJS, NestJS, ExpressJS, GraphQL
            \item \textbf{Testing \& Documentation:} Jest, Cypress, React Testing Library, Storybook
            \item \textbf{Version Control:} Git, GitHub, Bitbucket
            \item \textbf{Additional:} Core Web Vitals optimization, SEO, Figma, Jira, Confluence
        }
    \resumeSubHeadingListEnd

%-----------LEADERSHIP & AWARDS-----------
\section{Leadership \& Awards}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{99 Group Hackathon} $|$ \emph{Best UI/UX Design Award}}{2021}
        \resumeProjectHeading
            {\textbf{Quarterly Award Q2/21} $|$ \emph{Outstanding Performance}}{2021}
    \resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{Languages}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{English:} Professional proficiency
            \item \textbf{Bahasa Indonesia:} Native
            \item \textbf{Sundanese:} Native
        }
    \resumeSubHeadingListEnd

\end{document}