%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \small \textit{Frontend Engineer | Performance Optimization Specialist} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+6281313635148}{+62 81313635148} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{Performance-driven Frontend Engineer with 8+ years of experience building scalable, high-performance web applications across real estate, gaming, and travel industries. Proven track record in performance optimization, achieving measurable load time reductions and delivering responsive cross-device experiences. Deep technical foundation in JavaScript/TypeScript, performance optimization, and interactive UI development - skills directly applicable to creating engaging game experiences with smooth 60fps gameplay.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Core Languages \& Frameworks:} JavaScript (ES6+), TypeScript, HTML5/CSS3, React.js, React Native, Vue.js, Next.js, Redux.js, Node.js, Express.js
            \item \textbf{Performance \& Optimization:} Core Web Vitals optimization (LCP: 4.5s → 1.2s, 73\% improvement), Cross-device performance tuning, Bundle size optimization, SEO implementation
            \item \textbf{Development Practices:} Solution design, Technical architecture, Clean code principles, Git version control, Requirements translation to technical specifications
            \item \textbf{Build Tools \& Testing:} Webpack, Vite, Gulp.js, Jest, Cypress, React Testing Library, Storybook
            \item \textbf{Styling \& UI:} Tailwind CSS, SASS/SCSS, Styled Components, CSS-in-JS, Bootstrap, Figma
        }
    \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout, Bangkok, Thailand}{Mar 2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Revamped web application delivering 27\% increase in user traffic (Q3).}
                \resumeItem{Updated technology stacks achieving enhanced performance and security standards.}
                \resumeItem{Improved internal tools driving measurable operational productivity gains.}
                \resumeItem{Collaborated with UI/UX designers to transform complex designs into functional web elements.}
                \resumeItem{Built responsive applications optimized for peak performance across devices.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{AccelByte (AAA Gaming Developer Tools), Remote}{Jun 2022 -- Mar 2023}{}
            \resumeItemListStart
                \resumeItem{Developed SDKs and developer tools empowering AAA game development teams.}
                \resumeItem{Standardized developer experience achieving 40\% reduction in compilation time.}
                \resumeItem{Established component styling framework and documentation system using Storybook.}
                \resumeItem{Initiated knowledge-sharing sessions and code convention standardization.}
                \resumeItem{Created reusable component libraries ensuring consistent UI implementation.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99.co, Bandung, Indonesia}{Jul 2020 -- Jul 2022}{}
            \resumeItemListStart
                \resumeItem{Improved site performance reducing LCP from 4.5s to 1.2s (73\% improvement).}
                \resumeItem{Enhanced site traffic through strategic SEO improvements and schema validation.}
                \resumeItem{Maintained Core Web Vitals optimization for sustained peak performance.}
                \resumeItem{Recognized with "Own It" quarterly award (Q2/21) for exceptional product ownership.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com, Jakarta, Indonesia}{Aug 2019 -- Jul 2020}{}
            \resumeItemListStart
                \resumeItem{Implemented robust features using React, TypeScript, Redux for travel booking platform.}
                \resumeItem{Maintained comprehensive component documentation with Storybook.}
                \resumeItem{Conducted strategic refactoring initiatives for enhanced code scalability.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency, Bandung, Indonesia}{Jul 2018 -- Aug 2019}{}
            \resumeItemListStart
                \resumeItem{Developed comprehensive WordPress-based university platform (UPH).}
                \resumeItem{Built fully functional websites spanning backend to frontend implementation.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{SMK Negeri 7 Bandung} $|$ \emph{Analytical Chemistry}}{2009 -- 2011}
    \resumeSubHeadingListEnd

%-----------KEY ACHIEVEMENTS-----------
\section{Key Achievements}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{27\% increase in user traffic} (Q3) through web application revamp at PropertyScout
            \item \textbf{40\% reduction in compilation time} through developer tooling optimization at AccelByte
            \item \textbf{73\% LCP improvement (4.5s to 1.2s)} through systematic performance optimization at 99.co
            \item \textbf{Quarterly Award Q2/21} recipient for product ownership excellence
            \item \textbf{99 Group Hackathon - Best UI/UX Design} winner
        }
    \resumeSubHeadingListEnd

%-----------WHY GAME DEVELOPMENT-----------
\section{Why Game Development?}
\small{My extensive experience optimizing JavaScript performance, managing complex state systems, and ensuring smooth 60fps-level rendering across devices provides a powerful foundation for game development. At AccelByte, I developed tools for AAA game developers, gaining direct exposure to the gaming industry's demanding technical requirements and performance standards. I'm excited to apply my proven performance optimization expertise and deep JavaScript skills to creating engaging interactive experiences using Cocos Creator, bringing the same performance-first mindset that achieved 73\% load time improvements to delivering smooth, responsive gameplay.}

%-----------LANGUAGES-----------
\section{Languages}
    \resumeSubHeadingListStart
        \small{
            \item Bahasa Indonesia (Native), English (Professional), Sundanese (Native)
        }
    \resumeSubHeadingListEnd

\end{document}
