\documentclass[11pt]{letter}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{
  a4paper,
  left=20mm,
  right=20mm,
  top=20mm,
  bottom=20mm}

\signature{Kenni Gandira Alamsyah}
\address{
  Bangkok, Thailand \\
  +62 81313635148 \\
  devkenni.g@gmail.com \\
  \href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
}

\begin{document}

\begin{letter}{
  Hiring Manager \\
  Starcube Co., Ltd. \\
  Bangkok, Thailand
}

\opening{Dear Hiring Manager,}
I am excited to apply for the Frontend Developer (Games) position at Starcube Co., Ltd. With 8+ years of frontend engineering experience specializing in JavaScript/TypeScript and performance optimization, I am eager to transition my technical expertise into creating engaging interactive game experiences and learning Cocos Creator.

My background in high-performance web application development provides transferable skills for game development's core technical demands. At AccelByte, I developed SDKs and developer tools for AAA game developers, gaining valuable exposure to the gaming industry's technical standards and performance requirements. This experience, combined with my JavaScript expertise and optimization skills, positions me to learn quickly and contribute to your game development team.

My technical achievements reflect the performance-first mindset essential for delivering smooth gameplay. At 99.co, I contributed to a 73\% improvement in page load time (4.5s to 1.2s) through systematic optimization - the same performance principles that ensure consistent 60fps gameplay. At PropertyScout, I worked on improvements that resulted in a 27\% increase in user traffic, demonstrating my ability to build engaging, responsive experiences. At AccelByte, I helped achieve a 40\% reduction in compilation time through developer tooling enhancements, showcasing my commitment to workflow efficiency.

I am particularly drawn to Starcube because of the opportunity to apply my JavaScript expertise with Cocos Creator in a creative, interactive domain. While I'm new to game development specifically, my experience translating complex requirements into technical specifications, optimizing performance across devices, and implementing clean code practices will enable me to learn quickly and contribute to robust, high-performance games. I am enthusiastic about mastering game-specific development patterns while bringing my proven optimization skills and performance mindset to your team.

I would welcome the opportunity to discuss how my frontend engineering expertise and passion for performance optimization can support creating exceptional gaming experiences at Starcube.

Thank you for considering my application. I look forward to speaking with you about this opportunity.

\closing{Best regards,}

\end{letter}

\end{document}
