%-------------------------
% Cover Letter in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[11pt,a4paper]{letter}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

% Sender information
\signature{Kenni Gandira Alamsyah}
\address{
    Bangkok, Thailand \\
    +62 81313635148 \\
    \href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} \\
    \href{https://www.linkedin.com/in/kenni-g-alamsyah}{linkedin.com/in/kenni-g-alamsyah}
}

\begin{document}

\begin{letter}{
    Hiring Manager \\
    WiPay Co., Ltd. \\
    Bangkok, Thailand
}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Software Engineer (Frontend) position at WiPay Co., Ltd. With 8+ years of experience building scalable web applications using React, TypeScript, and modern JavaScript frameworks, I am excited about the opportunity to contribute to WiPay's fintech platform.

Your requirements for React/Redux, Vue.js, JavaScript, HTML5, and Node.js align well with my expertise. At PropertyScout, I contributed to a 27\% increase in user traffic through web application optimization. At AccelByte, I helped achieve a 40\% reduction in compilation time by standardizing developer tools and Webpack configurations. At 99.co, I contributed to performance improvements that reduced LCP from 4.5s to 1.2s through Core Web Vitals optimization.

I have experience with asynchronous and event-driven programming, build tools like Webpack, and version control with Git. My Node.js backend experience with Express.js and NestJS complements my frontend expertise, enabling me to contribute to full-stack development.

While my primary focus has been on responsive web development, I am eager to expand into mobile application development. My foundation in React and JavaScript, combined with my ability to learn new technologies, positions me to contribute effectively while growing in areas where WiPay needs support.

I am particularly drawn to WiPay's role in Thailand's fintech ecosystem and the opportunity to work on payment solutions that impact people's daily lives. I would welcome the chance to discuss how my frontend expertise can support WiPay's growth.

Thank you for considering my application.

\closing{Best regards,}

\end{letter}

\end{document}
