%-------------------------
% Cover Letter in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[11pt,a4paper]{letter}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

% Sender information
\signature{Kenni Gandira Alamsyah}
\address{
    Bangkok, Thailand \\
    +62 81313635148 \\
    \href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} \\
    \href{https://www.linkedin.com/in/kenni-g-alamsyah}{linkedin.com/in/kenni-g-alamsyah}
}

\begin{document}

\begin{letter}{
    Hiring Manager \\
    WiPay Co., Ltd. \\
    Bangkok, Thailand
}

\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Software Engineer (Frontend) position at WiPay Co., Ltd. With 8+ years of experience building scalable web applications using React, TypeScript, and modern JavaScript frameworks, I am excited about the opportunity to contribute to WiPay's fintech platform.

Your requirements for React/Redux, Vue.js, JavaScript, HTML5, and Node.js align perfectly with my expertise. At PropertyScout, I contributed to a 27\% increase in user traffic through web application optimization and responsive design. At AccelByte, I helped achieve a 40\% reduction in compilation time by standardizing developer tools and Webpack configurations. At 99.co, I improved site performance by optimizing Core Web Vitals, reducing LCP from 4.5s to 1.2s.

I have extensive experience with asynchronous and event-driven programming, build tools like Webpack, and version control with Git. My Node.js backend experience with Express.js and NestJS complements my frontend expertise, enabling me to contribute to full-stack development and API integration.

While my primary focus has been on responsive web development, I am eager to expand into mobile application development for iOS, Android, and Huawei platforms. My strong foundation in React and JavaScript, combined with my proven ability to quickly master new technologies, positions me well to contribute effectively while growing in areas where WiPay needs support.

I am particularly drawn to WiPay's role in Thailand's fintech ecosystem and the opportunity to work on payment solutions that impact people's daily lives. I would welcome the chance to discuss how my frontend expertise and commitment to performance optimization can support WiPay's continued growth.

Thank you for considering my application. I look forward to the opportunity to speak with you.

\closing{Best regards,}

\end{letter}

\end{document}
