%-------------------------
% Cover Letter in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}

\pagestyle{empty}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{#2}}}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header
\begin{flushleft}
{\Large \textbf{Kenni Gandira Alamsyah}} \\
\vspace{3pt}
\link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$ +66 0842704245 \\
Bangkok, Thailand
\end{flushleft}

\vspace{20pt}

% Date
\today

\vspace{20pt}

% Salutation
Dear Hiring Manager,

% Body
I am excited to apply for the Frontend Engineer position with your AI company through HireClout. With 8+ years of experience building user-centric interfaces and developing tools for both technical and non-technical users, I am eager to contribute to AI annotation workflows and model evaluation platforms.

Your mission to build interactive tools for complex annotation tasks aligns perfectly with my expertise. At PropertyScout, I built an internal campaign management tool serving 17+ team members, enabling non-technical stakeholders to confidently manage complex JSON structures across multiple environments. This transformed technical workflows into intuitive experiences---exactly the challenge annotation platforms face when empowering teams to efficiently label and evaluate AI training data.

The opportunity to ensure data integrity for large language models particularly excites me. My systematic approach to Core Web Vitals optimization---achieving a 73\% LCP improvement from 4.5s to 1.2s---demonstrates the precision and quality focus that annotation workflows demand. At AccelByte, I developed admin portals and tools for AAA game studios, mastering the art of presenting complex data clearly to diverse audiences---a skill critical for model evaluation interfaces.

I thrive in fast-paced, autonomous environments where proactive problem-solving drives results. My 40\% compilation time reduction at AccelByte came from recognizing inefficiencies and implementing solutions. At 99.co, my product ownership earned the Q2/21 ``Own It'' award and Best UI/UX Design at the 99 Group Hackathon.

I am passionate about leveraging AI advancements to solve complex challenges and would welcome the opportunity to discuss how my track record of building performant, intuitive tools can contribute to your team's mission.

Thank you for your consideration.

\vspace{10pt}

% Closing
Best regards, \\
Kenni Gandira Alamsyah

\end{document}
