%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \small Bangkok, Thailand $|$
    \link{https://api.whatsapp.com/send/?phone=+660842704245}{+66 0842704245} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
    \small{Results-driven Frontend Engineer with 8+ years of experience building scalable web applications across real estate, gaming, and travel industries. Proven track record of delivering measurable performance improvements and creating intuitive tools that empower both technical and non-technical users. Passionate about leveraging cutting-edge technologies to solve complex problems and enhance user experiences.}

%-----------KEY ACHIEVEMENTS-----------
\section{Key Achievements}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Delivered 27\% user traffic growth} (Q3) through comprehensive web application modernization at PropertyScout
            \item \textbf{Achieved 40\% compilation time reduction} by standardizing developer experience and build tooling at AccelByte
            \item \textbf{Optimized critical performance metrics}, reducing Largest Contentful Paint from 4.5s to 1.2s (73\% improvement) at 99.co
            \item \textbf{Recognized for excellence}: Q2/21 Quarterly Award recipient and Best UI/UX Design winner at 99 Group Hackathon
            \item \textbf{Built high-impact developer tools} serving 17+ team members and AAA game studios
        }
    \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Professional Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout}{March 2023 -- Present}{Bangkok, Thailand}
            \resumeItemListStart
                \resumeItem{Built and delivered internal campaign management tool enabling 17+ team members to configure complex JSON structures across multiple environments, transforming technical workflows into intuitive experiences for non-technical stakeholders.}
                \resumeItem{Led web application modernization that delivered 27\% increase in user traffic (Q3) through strategic technology stack updates and performance enhancements.}
                \resumeItem{Optimized operational productivity by developing intuitive internal tools that streamline workflows and reduce manual configuration overhead.}
                \resumeItem{Collaborated closely with UI/UX designers to transform design systems into pixel-perfect, functional web components.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{AccelByte}{June 2022 -- March 2023}{Remote}
            \resumeItemListStart
                \resumeItem{Developed tools and admin portal features for AAA game studios, creating interfaces that communicate complex data clearly to both technical and non-technical users.}
                \resumeItem{Achieved 40\% reduction in compilation time by standardizing developer experience, establishing build conventions, and optimizing tooling configurations.}
                \resumeItem{Established component styling standards and comprehensive documentation using Storybook, improving team efficiency and code consistency.}
                \resumeItem{Led knowledge-sharing initiatives including regular sessions and code convention standardization that elevated team technical capabilities.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99.co}{July 2020 -- July 2022}{Bandung, Indonesia}
            \resumeItemListStart
                \resumeItem{Optimized site performance, reducing Largest Contentful Paint from 4.5s to 1.2s (73\% improvement) through systematic Core Web Vitals optimization.}
                \resumeItem{Enhanced site traffic through strategic SEO improvements and schema validation implementation.}
                \resumeItem{Recognized with "Own It" Quarterly Award (Q2/21) for exceptional product ownership and technical contributions.}
                \resumeItem{Won Best UI/UX Design at 99 Group Hackathon, demonstrating design thinking and creative problem-solving capabilities.}
                \resumeItem{Maintained strong Core Web Vitals metrics, ensuring consistently excellent user experiences.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com}{August 2019 -- July 2020}{Jakarta, Indonesia}
            \resumeItemListStart
                \resumeItem{Delivered high-quality features using React, TypeScript, and Redux for one of Indonesia's leading travel platforms.}
                \resumeItem{Established component documentation standards with Storybook, improving developer onboarding and team collaboration.}
                \resumeItem{Conducted code refactoring initiatives to enhance scalability and maintainability of large-scale applications.}
                \resumeItem{Collaborated with product teams to optimize user experience and implement data-driven UX enhancements.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency}{July 2018 -- August 2019}{Bandung, Indonesia}
            \resumeItemListStart
                \resumeItem{Developed comprehensive WordPress-based platform for Universitas Pelita Harapan (UPH), delivering full-stack solutions from backend to frontend.}
                \resumeItem{Created flexible, customizable solutions addressing complex client requirements while maintaining code quality and performance.}
                \resumeItem{Delivered multiple websites with pixel-perfect implementation and responsive design.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Expertise}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Frontend Technologies:} React.js, Vue.js, Next.js, TypeScript, JavaScript, Redux.js, React Native, Electron.js
            \item \textbf{Styling \& Design:} CSS3, Tailwind CSS, SASS/SCSS, Styled Components, CSS-in-JS, Bootstrap
            \item \textbf{Performance \& Quality:} Core Web Vitals Optimization, SEO Implementation, Webpack, Vite, Jest, Cypress, React Testing Library
            \item \textbf{Tools \& Infrastructure:} Storybook, GraphQL, Node.js, Git, Figma, Elasticsearch
            \item \textbf{Collaboration:} Cross-functional collaboration, UI/UX partnership, mentorship, knowledge sharing
        }
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{SMK Negeri 7 Bandung} $|$ \emph{Analytical Chemistry}}{2009 -- 2011}
    \resumeSubHeadingListEnd

\end{document}
