%-------------------------
% Cover Letter in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}

\pagestyle{empty}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{#2}}}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Header
\begin{flushleft}
{\Large \textbf{Kenni Gandira Alamsyah}} \\
\vspace{3pt}
\link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$ +66 0842704245 \\
Bangkok, Thailand
\end{flushleft}

\vspace{20pt}

% Date
\today

\vspace{20pt}

% Salutation
Dear Hiring Manager,

% Body
I am writing to express my strong interest in the Frontend Engineer position at your AI company through HireClout. With 8+ years of experience building user-friendly interfaces and developer tools, I am excited about the opportunity to contribute to advancing AI annotation workflows and model evaluation tools.

Your focus on building interactive tools for complex annotation tasks resonates deeply with my experience. At PropertyScout, I developed an internal campaign management tool used by 17+ team members to configure complex JSON structures across multiple environments. This tool transformed how non-technical stakeholders interacted with technical configurations, similar to how annotation tools empower teams to efficiently label and evaluate AI training data. Additionally, I built a drag-and-drop UI builder that enabled users to create custom property listing components without coding---demonstrating my ability to make complex technical workflows accessible.

I am particularly drawn to the challenge of ensuring data integrity for large language models. My experience optimizing Core Web Vitals---contributing to a 27\% LCP improvement through systematic performance analysis---reflects the same attention to detail and quality that annotation workflows demand. At AccelByte, I built admin portal features and developer tools for game studios, gaining deep experience in creating interfaces that communicate complex data clearly to both technical and non-technical users.

The opportunity to work in a fast-paced, autonomous environment while exploring AI advancements aligns perfectly with my career trajectory. I thrive in collaborative settings where proactive problem-solving drives innovation, as evidenced by my work across real estate, gaming, and travel industries.

I would welcome the opportunity to discuss how my experience building performant, intuitive tools can contribute to your team's mission of advancing AI development through better annotation workflows.

Thank you for considering my application.

\vspace{10pt}

% Closing
Best regards, \\
Kenni Gandira Alamsyah

\end{document}
