% Cover Letter in LaTeX
% Simple Computer Modern Font Design

\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  top=25mm,
  bottom=25mm
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

% Header
\begin{center}
  \textbf{\Large Kenni Gandira Alamsyah}\\
  \vspace{0.5em}
  \href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$ +66 0842704245 $|$ \href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{center}

\vspace{1em}

\today

\vspace{1em}

Dear Hiring Manager,

I am writing to express my strong interest in the Front End Developer position at Dexon Technology. With 8+ years of experience building responsive web applications using React, Vue.js, and TypeScript, I am excited about the opportunity to contribute to your team in developing modern, high-performance user interfaces.

Your requirements for expertise in modern JavaScript frameworks, testing automation, and cross-browser solutions align perfectly with my professional experience. At PropertyScout, I revamped web applications resulting in a 27\% increase in user traffic while optimizing Core Web Vitals to achieve 1.2-second page load times. At AccelByte, I reduced compilation time by 40\% through build optimization and established component documentation standards using Storybook. My experience at 99.co demonstrates my commitment to performance, where I improved LCP from 4.5s to 1.2s and increased organic traffic by 87\%.

I am particularly drawn to Dexon Technology's focus on data visualization and 3D rendering capabilities. While I have extensive experience with React, Vue.js, Redux, and comprehensive testing tools like Jest and Cypress, I am eager to expand my expertise in charting libraries and Three.js for your visualization projects. My track record of quickly learning new technologies---from TypeScript migration at Tiket.com to game developer tools at AccelByte---demonstrates my ability to adapt and deliver quality solutions.

Having worked with international teams at AccelByte and now residing in Bangkok at PropertyScout, I bring strong English communication skills and experience collaborating across time zones. I value code quality, maintainability, and team collaboration, as evidenced by my quarterly awards and hackathon recognition for UI/UX excellence.

I would welcome the opportunity to discuss how my background in building scalable, performant web applications can contribute to Dexon Technology's continued success.

Thank you for considering my application. I look forward to speaking with you about this exciting opportunity.

\vspace{1em}

Best regards,

\vspace{1em}

Kenni Gandira Alamsyah

\end{document}
