% Cover Letter in LaTeX
% Simple Computer Modern Font Design

\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  top=25mm,
  bottom=25mm
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

% Header
\begin{center}
  \textbf{\Large Kenni Gandira Alamsyah}\\
  \vspace{0.5em}
  \href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$ +66 0842704245 $|$ \href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{center}

\vspace{1em}

\today

\vspace{1em}

Dear Hiring Manager,

I am eager to apply for the Front End Developer position at Dexon Technology. With 8+ years of experience building high-performance web applications using React, Vue.js, and TypeScript, I have demonstrated a track record of delivering measurable improvements through technical excellence and collaborative problem-solving.

Your requirements align well with my core expertise. At PropertyScout, I revamped web applications achieving a 27\% traffic increase while optimizing Core Web Vitals to 1.2-second page loads. At AccelByte, I delivered a 40\% compilation time improvement through build optimization and established comprehensive Storybook documentation standards. My performance optimization expertise is further demonstrated at 99.co, where I improved LCP from 4.5s to 1.2s and increased organic traffic by 87\%.

I am particularly interested in Dexon Technology's focus on data visualization and 3D rendering capabilities. While my primary expertise lies in React, Vue.js, Redux, and comprehensive testing tools (Jest, Cypress), my track record of rapidly adapting to new technologies---from TypeScript migration at Tiket.com to game developer tools at AccelByte---demonstrates my ability to quickly master charting libraries and Three.js for your visualization projects.

Having collaborated with international teams at AccelByte and currently working in Bangkok at PropertyScout, I bring strong English communication skills and proven cross-functional collaboration experience. My commitment to code quality and team excellence is evidenced by quarterly awards and hackathon recognition for UI/UX design.

I would welcome the opportunity to discuss how my expertise in building scalable, performant web applications can contribute to Dexon Technology's continued success.

Thank you for considering my application.

\vspace{1em}

Best regards,

\vspace{1em}

Kenni Gandira Alamsyah

\end{document}
