%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+660842704245}{+66 0842704245} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah/}
\end{center}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout (Real Estate Platform), Thailand}{2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Revamped web applications achieving 27\% increase in user traffic (Q3) through modern React implementation and comprehensive UX optimization.}
                \resumeItem{Optimized Core Web Vitals achieving 1.2-second page load time, significantly improving mobile and desktop performance metrics.}
                \resumeItem{Transformed Figma designs into production-ready, responsive, pixel-perfect components in collaboration with UI/UX design team.}
                \resumeItem{Integrated RESTful APIs for property listing platform, processing 17,000+ monthly updates.}
                \resumeItem{Enhanced internal development tools, improving operational productivity for the engineering team.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{AccelByte (Gaming Developer Tools), Indonesia}{2022 -- 2023}{}
            \resumeItemListStart
                \resumeItem{Developed game developer dashboard using React and TypeScript for AAA game studios.}
                \resumeItem{Reduced compilation time by 40\% (from 15 to 9 minutes) through Webpack configuration optimization and build process improvements.}
                \resumeItem{Established component styling standards and comprehensive documentation using Storybook for design system consistency.}
                \resumeItem{Optimized frontend performance by implementing efficient data fetching patterns and image asset optimization.}
                \resumeItem{Initiated knowledge-sharing sessions to standardize code conventions across the development team.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99.co (Real Estate Platform), Bandung, Indonesia}{2020 -- 2022}{}
            \resumeItemListStart
                \resumeItem{Improved Largest Contentful Paint (LCP) from 4.5s to 1.2s through Core Web Vitals optimization techniques.}
                \resumeItem{Enhanced site engagement by 25\% through performance improvements and responsive design enhancements.}
                \resumeItem{Increased organic traffic from 4,000 to 7,500 monthly visits (87\% growth) through SEO improvements and schema validation.}
                \resumeItem{Increased frontend team productivity by 30\% by creating reusable component library and comprehensive style guide.}
                \resumeItem{Received ``Own It'' quarterly award for exceptional product ownership and code quality.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com (Travel \& Hospitality), Jakarta, Indonesia}{2019 -- 2020}{}
            \resumeItemListStart
                \resumeItem{Implemented TypeScript migration from JavaScript, establishing type safety across the travel platform.}
                \resumeItem{Developed features using React, TypeScript, and Redux for booking and payment workflows.}
                \resumeItem{Maintained comprehensive component documentation with Storybook ensuring design consistency.}
                \resumeItem{Conducted regular code refactoring to improve scalability and maintainability.}
                \resumeItem{Coordinated with product team to enhance user experience based on customer feedback analysis.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency (now VML) (Marketing Agency), Bandung, Indonesia}{2018 -- 2019}{}
            \resumeItemListStart
                \resumeItem{Developed WordPress-based platform for Pelita Harapan University (UPH) serving 30,000+ students.}
                \resumeItem{Created responsive, cross-browser compatible solutions across multiple concurrent client projects.}
                \resumeItem{Built full-stack features integrating frontend components with backend PHP services.}
                \resumeItem{Delivered projects on time while maintaining high quality standards across diverse industry verticals.}
            \resumeItemListEnd

        \resumeSubheading
            {Web Developer}{Hazani Rangka Utama (IT Services), Bandung, Indonesia}{2017 -- 2018}{}
            \resumeItemListStart
                \resumeItem{Developed three commercial WordPress themes for ThemeForest marketplace generating 10,000+ total sales.}
                \resumeItem{Ensured W3C validation and accessibility compliance across all projects.}
                \resumeItem{Implemented responsive design patterns ensuring cross-browser compatibility.}
                \resumeItem{Managed customer support delivering theme customizations and bug resolutions.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{PT NTCI (Education and Ecommerce), Yogyakarta, Indonesia}{2016 -- 2017}{}
            \resumeItemListStart
                \resumeItem{Built e-learning and ticket booking applications using HTML5, CSS3, and JavaScript.}
                \resumeItem{Contributed to expanding development team from 3 to 15 members through recruiting efforts.}
                \resumeItem{Participated in establishing development standards and best practices for code quality.}
                \resumeItem{Balanced dual role as frontend developer and UI/UX designer across multiple projects.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Proficient:} ReactJS, VueJS, NextJS, NuxtJS, Tailwind CSS, Redux, React Query, Javascript, Typescript, CSS3, HTML5
            \item \textbf{Familiar:} NodeJS, PHP, REST API, GraphQL, Storybook, Cypress, React Testing Library, Jest, Webpack, Vite, Bootstrap
        }
    \resumeSubHeadingListEnd

%-----------LEADERSHIP & AWARDS-----------
\section{Leadership \& Awards}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{99 Group Hackathon} $|$ \emph{Best UI/UX Design Award}}{2021}
        \resumeProjectHeading
            {\textbf{Quarterly Award Q2/21} $|$ \emph{Outstanding Performance}}{2021}
    \resumeSubHeadingListEnd

\end{document}
