% Cover Letter in LaTeX
% Simple Computer Modern Font Design

\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  top=25mm,
  bottom=25mm
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

% Header
\begin{center}
  \textbf{\Large Kenni Gandira Alamsyah}\\
  \vspace{0.5em}
  \href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$ +66 0842704245 $|$ \href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{center}

\vspace{1em}

\today

\vspace{1em}

Dear Hiring Manager,

I am excited to apply for the Front End Developer position at Dexon Technology. With 8+ years of proven success building high-performance web applications using React, Vue.js, and TypeScript, I bring a track record of delivering measurable business impact through technical excellence and innovative problem-solving.

Your requirements align perfectly with my core expertise. At PropertyScout, I architected a web application revamp that drove a 27\% traffic increase while optimizing Core Web Vitals to achieve exceptional 1.2-second page loads. At AccelByte, I delivered a 40\% compilation time improvement through build optimization and established comprehensive Storybook documentation standards. My performance optimization expertise is further demonstrated at 99.co, where I accelerated LCP from 4.5s to 1.2s and drove 87\% organic traffic growth.

I am particularly energized by Dexon Technology's focus on data visualization and 3D rendering capabilities. My extensive React and Vue.js experience, combined with mastery of Redux, comprehensive testing tools (Jest, Cypress), and responsive design principles, provides a strong foundation for your visualization projects. My proven ability to rapidly master new technologies---from leading TypeScript migration at Tiket.com to building game developer tools at AccelByte---positions me to quickly excel with charting libraries and Three.js.

Having collaborated with international teams at AccelByte and currently working in Bangkok at PropertyScout, I bring strong English communication skills and proven cross-functional collaboration experience. My commitment to code quality and team excellence is evidenced by quarterly awards and hackathon recognition for UI/UX design.

I am confident my expertise in building scalable, performant web applications will drive significant value for Dexon Technology's continued growth and innovation.

Thank you for considering my application. I look forward to discussing how I can contribute to your team's success.

\vspace{1em}

Best regards,

\vspace{1em}

Kenni Gandira Alamsyah

\end{document}
