% Cover Letter in LaTeX
% Simple Computer Modern Font Design

\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  top=25mm,
  bottom=25mm
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

% Header
\begin{center}
  \textbf{\Large Kenni Gandira Alamsyah}\\
  \vspace{0.5em}
  \href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$ +66 0842704245 $|$ \href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{center}

\vspace{1em}

\today

\vspace{1em}

Dear Hiring Manager,

I am writing to express my interest in the Front End Developer position at Dexon Technology. With 8+ years of experience building web applications using React, Vue.js, and TypeScript, I believe I could contribute meaningfully to your team's projects.

Your requirements align well with my technical background. At PropertyScout, I contributed to a web application revamp that helped achieve a 27\% traffic increase while working on Core Web Vitals optimization. At AccelByte, I was part of a team effort that reduced compilation time by 40\% through build optimization. My experience at 99.co involved contributing to performance improvements that brought LCP from 4.5s to 1.2s.

I am particularly interested in Dexon Technology's focus on data visualization and 3D rendering capabilities. While I haven't yet worked directly with charting libraries or Three.js, my React and Vue.js experience, combined with knowledge of Redux, testing tools (Jest, Cypress), and responsive design principles, provides a foundation I can build upon. My track record of adapting to new technologies---from working with TypeScript at Tiket.com to building game developer tools at AccelByte---demonstrates my ability to learn quickly.

Having worked with international teams at AccelByte and currently based in Bangkok at PropertyScout, I am comfortable collaborating in English across different time zones. My commitment to code quality has been recognized through quarterly awards and hackathon recognition for UI/UX design.

I would welcome the opportunity to discuss how my skills and experience could support Dexon Technology's continued growth.

Thank you for considering my application.

\vspace{1em}

Best regards,

\vspace{1em}

Kenni Gandira Alamsyah

\end{document}
