\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{parskip}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  bottom=25mm,
  top=25mm
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{\Large Kenni Gandira Alamsyah} \\[0.3em]
devkenni.g@gmail.com $|$ +62 81313635148 $|$ Bangkok, Thailand \\
LinkedIn: linkedin.com/in/kenni-g-alamsyah
\end{flushleft}

\vspace{1.5em}

\begin{flushleft}
\today
\end{flushleft}

\vspace{1em}

\begin{flushleft}
Hiring Manager \\
Mekari \\
Jakarta, Indonesia
\end{flushleft}

\vspace{1em}

\textbf{RE: Senior Software Engineer 1 - Frontend}

\vspace{1em}

Dear Hiring Manager,

I am writing to express my strong interest in the Senior Software Engineer 1 - Frontend position at Mekari. With 8+ years of experience building scalable web applications and a proven track record in performance optimization, I am excited about the opportunity to contribute to Indonesia's leading SaaS platform serving over 1 million users.

Mekari's mission to accelerate digital transformation for Indonesian entrepreneurs resonates deeply with my experience in delivering impactful solutions. I have worked extensively with TypeScript and React.js to build large-scale applications across real estate, gaming, and travel industries. My expertise in Vue.js, combined with my proficiency in modern testing frameworks like Jest and Cypress, aligns perfectly with your technical requirements.

At PropertyScout, I revamped web applications that resulted in a 27\% increase in user traffic. At AccelByte, I standardized the developer experience and achieved a 40\% reduction in compilation time through build optimization. At 99.co, I improved Core Web Vitals by reducing LCP from 4.5s to 1.2s, demonstrating my commitment to performance excellence. These achievements reflect my ability to deliver measurable business impact through technical innovation.

I am particularly drawn to Mekari's ecosystem approach with Jurnal, Talenta, Qontak, and Flex. The opportunity to work on products impacting thousands of businesses excites me. My experience mentoring developers and establishing knowledge-sharing practices aligns with your emphasis on team collaboration and technical documentation. I bring strong architectural problem-solving skills and a passion for building solutions that delight customers.

I would welcome the opportunity to discuss how my background in building performant, scalable web applications can contribute to Mekari's continued growth and success.

Thank you for considering my application. I look forward to speaking with you about this exciting opportunity.

\vspace{1em}

Best regards,

\vspace{1em}

Kenni Gandira Alamsyah

\end{document}
