\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage{xcolor}

\geometry{
  a4paper,
  left=10mm,
  right=10mm,
  bottom=13mm,
  top=13mm
}

\pagestyle{empty}

%%%%%%%%%%%% Change your first/lastname below %%%%%%%%%%%%

\newcommand{\firstname}{Kenni Gandira}
\newcommand{\lastname}{Alamsyah}

%%%%%%%%%%%%% Macros %%%%%%%%%%%%%

%%%%%%%%%%%%% Colors %%%%%%%%%%%%%

\definecolor{blueSky}{RGB}{49, 120, 198}
\definecolor{orangeFruit}{RGB}{224, 128, 44}
\definecolor{redBlood}{RGB}{188, 20, 20}
\definecolor{grayShy}{RGB}{153, 150, 142}

\newcommand{\mainColor}{redBlood} % pick a color above, or add a custom one

%%%%%%%%%%%%% Spaces %%%%%%%%%%%%%

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

% Horizontal %

\newcommand{\xhspace}{\hspace*{0.1em}}
\newcommand{\shspace}{\hspace*{0.8em}}

% Vertical %

\newcommand{\xvspace}{\vspace*{0.1em}}
\newcommand{\svspace}{\vspace*{0.5em}}
\newcommand{\mvspace}{\vspace*{1.5em}}
\newcommand{\hvspace}{\vspace*{2.5em}}

\newcommand{\negxvspace}{\vspace*{-0.2em}}
\newcommand{\negsvspace}{\vspace*{-0.5em}}
\newcommand{\negmvspace}{\vspace*{-1em}}
\newcommand{\neghvspace}{\vspace*{-1.5em}}

%%% Personal Details Macro %%%

\newcommand{\userInfo}[4]{
    \begin{flushleft}
        \color{\mainColor}
        \Huge
        \textbf{\MakeUppercase{\lastname}}
        \color{black}
        \textbf{\firstname}
        \color{\mainColor}
        \noindent\rule{19.1cm}{0.8pt}
        \color{grayShy}
        \small
        \par
        \parbox{7\spacebox} {
            \faMap \shspace #1 - #2 \par \svspace
            \faPhone \shspace #3 \par \svspace
            \faEnvelopeOpen \shspace \texttt{#4} \par \svspace
        }
        \color{\mainColor}
        \mvspace
    \end{flushleft}
    \negmvspace
}

%%% Company Details Macro %%%

\newcommand{\companyInfo}[4]{
    \begin{flushright}
        \parbox{4\spacebox}{
            \raggedleft
            \small
            \textbf{#1}\par
            \mvspace
            \color{grayShy} \textsc{\MakeLowercase{#2}}\par
            \xvspace
            \textsc{\MakeLowercase{#3}}\par
            \xvspace
            \textsc{\MakeLowercase{#4}}\par
            \color{black}
        }
    \end{flushright}
    \hvspace
}

%%% RE Macro %%%

\newcommand{\object}[1]{
    \small
    \color{\mainColor} \textbf{RE :} \color{black} \textbf{#1} \par
}

%%% Content Macro %%%

\newcommand{\content}[2]{
    \mvspace
    \begin{flushleft}
        \parbox{10.3\spacebox}{
          #1\par
          \svspace
          #2
        }\par
    \end{flushleft}
}

%%% Signature Macro %%%

\newcommand{\signature}{
    \svspace
    \parbox{3\spacebox}{
      Sincerely,\par
      \svspace \hspace{-0.3em}
      \textbf{\color{\mainColor} \MakeUppercase{\lastname} \color{black} \firstname}\par
      \svspace \svspace
      \Huge \faPenNib\par
    }\par
}

%%%%%%%%%%%% Your cover letter below %%%%%%%%%%%%

\begin{document}
\fontfamily{cmr}\selectfont
\userInfo{Bangkok, Thailand}{(Open to relocation)}{+62 81313635148}{devkenni.g@gmail.com}
\companyInfo{Baldur Connect}{Hiring Manager}{Stuttgart, Germany}{d.alzate@baldurconnect.com}
\object{Frontend Developer (JS/TypeScript) Position}
\content{
  Dear Hiring Manager, \\

  I am writing to express my strong interest in the Frontend Developer (JS/TypeScript) position at Baldur Connect. With 8+ years of experience as a Frontend Engineer specializing in JavaScript, TypeScript, and React, I am excited about the opportunity to contribute to digitizing communication in traditional industries and supporting your mission to serve major European banks and energy providers. \\

  Your focus on digitizing traditional industries strongly resonates with my experience. At PropertyScout, I contributed to transforming the real estate industry by helping revamp web applications that contributed to a 27\% increase in user traffic through collaborative team efforts. Similarly, at 99.co, I worked on modernizing property platforms, helping improve Core Web Vitals and contributing to reducing LCP from 4.5s to 1.2s. This experience in digitizing traditional sectors like real estate directly aligns with your work in banking and energy industries. \\

  My technical expertise matches your requirements perfectly. I have extensive experience with JavaScript and TypeScript (8+ years), React ecosystem development, and modern containerization practices including Docker. Having worked remotely for international companies and across different countries (Thailand, Indonesia), I bring strong collaboration skills essential for your diverse, 30+ nationality team environment. My experience with Agile/Scrum methodologies, code reviews, and pair programming at companies like AccelByte and PropertyScout demonstrates my ability to thrive in collaborative development environments. \\

  I am particularly drawn to Baldur Connect's commitment to employee growth through your Software Engineering Training Academy and your international, family-friendly workplace culture. The opportunity to relocate to Stuttgart and contribute to serving 1500+ customers across major European institutions is incredibly appealing. My international work experience and current English proficiency, combined with my willingness to improve my German language skills, position me well for this role. \\

  The collaborative work I contributed to at AccelByte, which helped achieve a 40\% reduction in compilation time through team-based build optimization, demonstrates my ability to contribute to your continuous integration and refactoring initiatives from day one. \\

}{I would welcome the opportunity to discuss how my background in building scalable, performant web applications for traditional industries can contribute to Baldur Connect's continued success in digitizing communication across European markets. Thank you for considering my application. I look forward to speaking with you about this exciting opportunity.}
\signature
\end{document}>