%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah (Enhanced based on Terrence Kuo's Résumé Tips)
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+6281313635148}{+62 81313635148} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah/} \\ \vspace{4pt}
    Bangkok, Thailand (Open to relocation to Stuttgart, Germany)
\end{center}

%-----------PROFILE-----------
\section{Profile}
\vspace{2pt}
\small{Frontend Engineer with 8+ years of experience in JavaScript and TypeScript, specializing in React ecosystem and scalable web applications for real estate, gaming, and travel industries. Strong background in Agile/Scrum methodologies, code reviews, and pair programming. Contributed to solutions that helped increase user traffic by 27\% and reduce compilation time by 40\% through collaborative team efforts.}
\vspace{10pt}

%-----------CORE COMPETENCIES-----------
\section{Core Competencies}
\vspace{2pt}
\small{
\begin{itemize}[leftmargin=0.15in, label=$\bullet$]
    \item JavaScript/TypeScript (8+ years) • React, Next.js, Redux, Vue.js
    \item Agile/Scrum methodologies • Code reviews \& pair programming
    \item Performance optimization \& Core Web Vitals • Docker containerization experience
    \item RESTful APIs \& GraphQL • Responsive design \& accessibility
\end{itemize}
}
\vspace{5pt}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout (Real Estate Platform), Thailand}{2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Contributed to revamping web applications using \textbf{React} and \textbf{TypeScript}, helping achieve a \textbf{27\% increase in user traffic} (Q3) through collaborative team development.}
                \resumeItem{Participated actively in \textbf{Agile/Scrum} environment with daily standups, sprint planning, and comprehensive code reviews.}
                \resumeItem{Helped update technology stacks for optimal performance and security in modern containerized environments.}
                \resumeItem{Contributed to improving internal tools for enhanced operational productivity through collaborative development and \textbf{pair programming} sessions.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{AccelByte (Gaming Developer Tools), Remote}{2022 -- 2023}{}
            \resumeItemListStart
                \resumeItem{Participated in developing tools for AAA game developers using \textbf{React} and \textbf{TypeScript} in collaborative team environment.}
                \resumeItem{Contributed to standardizing developer experience, helping achieve \textbf{40\% reduction in compilation time} through build optimization and team collaboration.}
                \resumeItem{Helped establish component styling and documentation using \textbf{Storybook} for collaborative development across the team.}
                \resumeItem{Participated in knowledge-sharing sessions and code convention standardization in \textbf{Agile} team environment.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99.co (Real Estate Platform), Bandung, Indonesia}{2020 -- 2022}{}
            \resumeItemListStart
                \resumeItem{Contributed to site performance improvements, helping reduce \textbf{LCP from 4.5s to 1.2s} through Core Web Vitals optimization and team collaboration.}
                \resumeItem{Helped enhance site traffic through SEO improvements and schema validation using modern JavaScript frameworks.}
                \resumeItem{Received "Own It" award for product ownership and collaborative development approach in team environment.}
                \resumeItem{Contributed to maintaining Core Web Vitals optimization and performance monitoring in \textbf{Agile methodology} with regular sprint cycles.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com (Travel \& Hospitality), Jakarta, Indonesia}{2019 -- 2020}{}
            \resumeItemListStart
                \resumeItem{Participated in implementing features using \textbf{React}, \textbf{TypeScript}, and \textbf{Redux} in collaborative team environment.}
                \resumeItem{Helped maintain component documentation with \textbf{Storybook} for team consistency and collaborative development.}
                \resumeItem{Contributed to regular refactoring for code scalability and maintainability through \textbf{code reviews} and \textbf{pair programming}.}
                \resumeItem{Collaborated with product team for UX enhancements in \textbf{Agile} development cycles.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency (now VML), Bandung, Indonesia}{2018 -- 2019}{}
            \resumeItemListStart
                \resumeItem{Participated in developing WordPress-based university platform (UPH) with modern JavaScript frameworks and collaborative development practices.}
                \resumeItem{Contributed to creating customizable solutions for complex requirements using team collaboration and agile methodologies.}
            \resumeItemListEnd

        \resumeSubheading
            {Web Developer}{Hazani Rangka Utama (Hartama), Bandung, Indonesia}{2017 -- 2018}{}
            \resumeItemListStart
                \resumeItem{Contributed to developing three WordPress themes for ThemeForest marketplace with focus on user experience and accessibility.}
                \resumeItem{Participated in W3C validation and accessibility compliance standards in collaborative team environment.}
            \resumeItemListEnd

        \resumeSubheading
            {Front End Developer}{PT NTCI, Yogyakarta, Indonesia}{2016 -- 2017}{}
            \resumeItemListStart
                \resumeItem{Started career as software engineer building foundational skills in JavaScript and React development.}
                \resumeItem{Contributed to building multiple projects including e-learning and ticket booking applications with team collaboration.}
                \resumeItem{Participated in interviewing and recruiting frontend developers, gaining collaborative leadership experience.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Frontend Technologies:} JavaScript (ES6+), TypeScript, HTML5, CSS3, React.js, Next.js, Vue.js, Redux.js \\
     \textbf{Styling \& Design:} CSS3, Tailwind CSS, SASS/SCSS, Styled Components, CSS-in-JS, Bootstrap, Responsive Design \\
     \textbf{Testing \& Documentation:} Jest, Cypress, React Testing Library, Storybook \\
     \textbf{Backend \& APIs:} Node.js, NestJS, Express.js, GraphQL, RESTful services, CodeIgniter \\
     \textbf{Development Practices:} Agile/Scrum, Code reviews, Pair programming, Git workflows \\
     \textbf{Build Tools \& DevOps:} Webpack, Gulp.js, npm, Vite, Docker (containerized environments) \\
     \textbf{Performance \& SEO:} Core Web Vitals optimization, SEO implementation \\
     \textbf{Additional:} WordPress, Strapi.js, OctoberCMS, Figma, Jira, Confluence
    }}
 \end{itemize}

%-----------KEY ACHIEVEMENTS-----------
\section{Key Achievements}
\vspace{2pt}
\small{
\begin{itemize}[leftmargin=0.15in, label=$\bullet$]
    \item Contributed to solutions that helped achieve \textbf{27\% increase in user traffic} (Q3) through web application revamp at PropertyScout
    \item Participated in team efforts that resulted in \textbf{40\% reduction in compilation time} through developer experience improvements at AccelByte
    \item Contributed to \textbf{LCP improvement from 4.5s to 1.2s} through Core Web Vitals optimization at 99.co
    \item \textbf{Quarterly Award Q2/21} recipient and \textbf{99 Group Hackathon - Best UI/UX Design} winner
    \item \textbf{International Experience:} Successfully collaborated across Thailand, Indonesia with remote and multinational teams
\end{itemize}
}
\vspace{5pt}

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {SMK Negeri 7 Bandung (High School)}{Analytical Chemistry}{2009 -- 2011}{}
    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\vspace{2pt}
\small{
\begin{itemize}[leftmargin=0.15in, label=$\bullet$]
    \item Certificate of completion - GDPR • Anti Bribery \& Corruption • Anti-Harassment and Discrimination
    \item Web Development HTML CSS \& SEO Certification • Anti-Money Laundering
\end{itemize}
}
\vspace{5pt}

%-----------LANGUAGES-----------
\section{Languages}
\vspace{2pt}
\small{
\begin{itemize}[leftmargin=0.15in, label=$\bullet$]
    \item \textbf{English:} Professional working proficiency • \textbf{Bahasa Indonesia:} Native • \textbf{Sundanese:} Native
    \item \textbf{German:} Basic (Currently learning - motivated to improve for Stuttgart role)
\end{itemize}
}

\end{document}