\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{parskip}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  bottom=25mm,
  top=25mm
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Kenni Gandira Alamsyah}\\
Bangkok, Thailand\\
devkenni.g@gmail.com\\
+66 0842704245
\end{flushleft}

\vspace{1em}

\begin{flushleft}
CSG Systems International\\
Hiring Manager\\
Lead Frontend Engineer Position
\end{flushleft}

\vspace{1em}

Dear Hiring Manager,

\vspace{0.5em}

I am excited to apply for the Lead Frontend Engineer position at CSG. With 8+ years of experience building scalable web applications and driving technical excellence through leadership, I am eager to contribute to the CSQ Quote \& Order platform and help modernize telecommunications and banking industries through innovative frontend solutions.

\vspace{0.5em}

CSG's mission to channel "the power of all" to create extraordinary experiences resonates deeply with my engineering philosophy. Your commitment to continuous learning, technical excellence, and team empowerment aligns perfectly with my track record of improving developer experience while delivering measurable business impact. I'm particularly energized by the opportunity to balance 50\% hands-on coding with technical leadership—precisely where I thrive, combining strategic vision with hands-on implementation.

\vspace{0.5em}

My experience delivering performance breakthroughs and leading technical initiatives demonstrates my readiness to drive impact at CSG. At PropertyScout, I drove a web application revamp that delivered a 27\% increase in user traffic. At AccelByte, I optimized developer experience achieving a 40\% reduction in compilation time (from 15 to 9 minutes), dramatically improving team productivity. At 99.co, I optimized Core Web Vitals reducing LCP by 73\% (from 4.5s to 1.2s), earning the "Own It" award for product ownership excellence and winning Best UI/UX Design at the 99 Group Hackathon in a competitive company-wide competition.

\vspace{0.5em}

While my deep expertise is in React and TypeScript ecosystems, I've successfully navigated framework transitions throughout my career—from Vue.js to React and across diverse technology stacks—demonstrating the adaptability that will accelerate my contribution to your Angular and micro-frontend architecture. My experience building component libraries, establishing Storybook documentation standards, and developing modular architectures provides a robust foundation for working with web components and modern frontend systems. Additionally, my proven track record establishing code conventions, mentoring engineering teams, and championing clean code through thorough PR reviews positions me to help define UI/X development standards and serve as a technical multiplier for your team.

\vspace{0.5em}

I would welcome the opportunity to discuss how my expertise in performance optimization, team development, and building scalable applications can contribute to CSG's innovation in the Quote \& Order platform and drive measurable impact for your customers.

\vspace{0.5em}

Thank you for considering my application.

\vspace{1em}

Best regards,\\
Kenni Gandira Alamsyah

\end{document}
