\documentclass[11pt]{letter}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{linkcolor}{HTML}{096dd9}
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
}

\signature{Kenni Gandira Alamsyah}
\address{Kenni Gandira Alamsyah \\ Bangkok, Thailand \\ +66 81313635148 \\ devkenni.g@gmail.com}

\begin{document}

\begin{letter}{SII Poland \\ Hiring Manager \\ Frontend Developer Position}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Frontend Developer position at SII Poland. With 8+ years of experience building web applications using React, TypeScript, and modern JavaScript frameworks, I am excited about the opportunity to contribute to SII's expansion in Thailand and support your mission of delivering innovative technology consulting solutions.

SII's commitment to building multithreaded, distributed software systems for enterprise clients aligns well with my experience in developing scalable, performance-optimized applications. At PropertyScout, I worked on a web application revamp that contributed to a 27\% increase in user traffic through performance enhancements and improved user experience. At AccelByte, I helped optimize build processes for AAA game development tools, contributing to a 40\% reduction in compilation time and improved developer productivity. At 99.co, I worked with the team to improve Core Web Vitals, helping reduce LCP from 4.5s to 1.2s through code splitting and optimization techniques.

My experience with React (8+ years), TypeScript, and collaborative Scrum environments could make me a good fit for this role. I have worked on integrating frontend applications with backend services using RESTful APIs and GraphQL, participated in comprehensive testing and debugging with Jest and Cypress, and contributed to delivering high-quality code through rigorous code reviews and continuous improvement practices. Having worked remotely and in cross-functional teams across multiple companies, I understand the importance of clear communication and knowledge sharing in distributed environments.

I am drawn to SII Poland's focus on technology consulting and digital transformation. My background in optimizing developer experience, establishing coding standards, and mentoring team members aligns with your need for engineers who can contribute to both technical excellence and team collaboration.

I would welcome the opportunity to discuss how my experience in building scalable, performant web applications might support SII Poland's growth in the Thai market and contribute to your clients' success.

Thank you for considering my application. I look forward to speaking with you about this opportunity.

\closing{Best regards,}

\end{letter}

\end{document}
