%-------------------------
% Resume in Latex
% Author: Kenni Gandira Alamsyah
%------------------------

\documentclass[a4paper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{xcolor}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.987\textwidth}[t]{
  >{\raggedright\arraybackslash}X
  >{\centering\arraybackslash}X
  >{\raggedleft\arraybackslash}X }
      \textbf{#1} & #2 & #3 \\
    \end{tabularx}
    \textit{\small#4}\\
    \vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.987\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.22in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-20pt}}

\newcommand{\link}[2]{{\color[HTML]{096dd9}\href[pdfnewwindow=true]{#1}{\small{#2}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenni Gandira Alamsyah} \\ \vspace{8pt}
    \link{https://api.whatsapp.com/send/?phone=+6681313635148}{+66 81313635148} $|$
    \link{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com} $|$
    \link{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah/}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
    \small{Frontend Engineer with 8+ years of experience building web applications using React, TypeScript, and modern JavaScript frameworks. Contributed to scalable solutions in Scrum environments, participated in application performance optimization, and worked with cross-functional teams. Experience creating responsive interfaces while maintaining code quality through comprehensive testing and debugging.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
    \resumeSubHeadingListStart
        \small{
            \item \textbf{Core Technologies:} React.js, TypeScript, JavaScript (ES6+), Next.js, Vue.js, HTML5, CSS3
            \item \textbf{State \& Testing:} Redux, Redux Toolkit, Context API, Jest, Cypress, React Testing Library
            \item \textbf{Build \& Tools:} Webpack, Vite, Gulp.js, npm, Git, GitHub, Bitbucket, Storybook
            \item \textbf{UI \& Styling:} Tailwind CSS, Styled Components, SASS/SCSS, Bootstrap, Figma
            \item \textbf{Backend Integration:} Node.js, GraphQL, Express.js, RESTful APIs
            \item \textbf{Methodologies:} Scrum/Agile, Code Review, CI/CD, Core Web Vitals optimization, SEO
        }
    \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Software Engineer}{PropertyScout, Thailand}{2023 -- Present}{}
            \resumeItemListStart
                \resumeItem{Contributed to web application revamp using React and TypeScript, which resulted in 27\% increase in user traffic (Q3).}
                \resumeItem{Worked with team to update technology stacks for optimal performance and security.}
                \resumeItem{Helped improve internal tools for enhanced operational productivity.}
                \resumeItem{Collaborated with UI/UX designers in Scrum environment to transform designs into functional web elements.}
                \resumeItem{Integrated frontend applications with backend services using RESTful APIs and GraphQL.}
                \resumeItem{Participated in code reviews and debugging sessions to maintain high-quality standards.}
            \resumeItemListEnd

        \resumeSubheading
            {Software Engineer}{AccelByte, Remote}{2022 -- 2023}{}
            \resumeItemListStart
                \resumeItem{Worked on developing tools for AAA game developers using React and TypeScript.}
                \resumeItem{Contributed to standardizing developer experience, helping achieve 40\% reduction in compilation time.}
                \resumeItem{Helped establish component styling and documentation using Storybook.}
                \resumeItem{Participated in knowledge-sharing sessions and code convention standardization.}
                \resumeItem{Worked in Scrum sprints and collaborated with cross-functional teams.}
                \resumeItem{Assisted in debugging complex UI/backend integration issues in high-traffic gaming platform.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{99.co, Indonesia}{2020 -- 2022}{}
            \resumeItemListStart
                \resumeItem{Worked with team to improve site performance, helping reduce LCP from 4.5s to 1.2s through optimization techniques.}
                \resumeItem{Contributed to enhancing site traffic through SEO improvements and schema validation.}
                \resumeItem{Received "Own It" award (Q2/21) for product ownership and quality contributions.}
                \resumeItem{Participated in Core Web Vitals optimization and performance monitoring.}
                \resumeItem{Built reusable React components with TypeScript for property listing platform.}
                \resumeItem{Collaborated in Scrum environment with designers and backend engineers.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Engineer}{Tiket.com, Indonesia}{2019 -- 2020}{}
            \resumeItemListStart
                \resumeItem{Implemented features using React, TypeScript, and Redux for travel booking platform.}
                \resumeItem{Maintained component documentation with Storybook.}
                \resumeItem{Participated in regular refactoring for code scalability and maintainability.}
                \resumeItem{Coordinated with product team for UX enhancements.}
                \resumeItem{Contributed to code reviews and testing practices.}
            \resumeItemListEnd

        \resumeSubheading
            {Frontend Developer}{Mirum Agency, Indonesia}{2018 -- 2019}{}
            \resumeItemListStart
                \resumeItem{Developed WordPress-based university platform (UPH).}
                \resumeItem{Created customizable solutions for complex requirements.}
                \resumeItem{Built fully functional websites from backend to frontend.}
                \resumeItem{Collaborated with designers and clients in agile workflow.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{SMK Negeri 7 Bandung} $|$ \emph{Analytical Chemistry}}{2009 -- 2011}
    \resumeSubHeadingListEnd

%-----------LEADERSHIP & AWARDS-----------
\section{Leadership \& Awards}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{99 Group Hackathon} $|$ \emph{Best UI/UX Design Award}}{2021}
        \resumeProjectHeading
            {\textbf{Quarterly Award Q2/21} $|$ \emph{Outstanding Performance}}{2021}
    \resumeSubHeadingListEnd

\end{document}
