\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  bottom=25mm,
  top=25mm
}

\pagestyle{empty}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\begin{document}

\begin{flushleft}
\textbf{\Large Kenni Gandira Alamsyah}\\
\vspace{4pt}
devkenni.g@gmail.com $|$ +66 0842704245\\
Bangkok, Thailand\\
\end{flushleft}

\vspace{12pt}

\today

\vspace{12pt}

\begin{flushleft}
Hiring Manager\\
Relevance AI\\
Sydney, Australia\\
\end{flushleft}

\vspace{12pt}

\textbf{RE: Senior Software Engineer Position}

\vspace{12pt}

Dear Hiring Manager,

\vspace{8pt}

I'm excited to apply for the Senior Software Engineer position at Relevance AI. With 8+ years building high-performance applications in TypeScript and Node.js, I'm eager to contribute to your mission of democratizing AI workforce automation.

\vspace{8pt}

Your vision to empower anyone to build AI agents resonates strongly with my experience creating developer tools that amplify team productivity. At AccelByte, I developed tools for AAA game studios and achieved a 40\% reduction in compilation time through systematic optimization. At PropertyScout, I delivered a 27\% user traffic increase through application modernization. At 99.co, I improved site performance by reducing LCP from 4.5s to 1.2s, demonstrating my commitment to technical excellence.

\vspace{8pt}

What distinguishes my approach is balancing rapid shipping with uncompromising quality standards. I thrive in fast-paced environments where innovation meets rigor---exactly what's needed to build enterprise-grade AI automation tools. My expertise with TypeScript, Node.js, and Vue.js aligns directly with your tech stack, while my track record of mentoring engineers and initiating knowledge-sharing sessions positions me to help shape your engineering culture.

\vspace{8pt}

I'm passionate about working at the forefront of AI innovation with a talented, nimble team. The opportunity to build tools that transform how people work---combined with solving complex problems in AI agent systems---is what drives me as an engineer.

\vspace{8pt}

I'm confident I can contribute meaningfully to Relevance AI's continued success and would welcome the opportunity to discuss how my background aligns with your team's needs.

\vspace{8pt}

Thank you for considering my application.

\vspace{12pt}

Best regards,

\vspace{8pt}

Kenni Gandira Alamsyah

\end{document}
