\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  bottom=25mm,
  top=25mm
}

\pagestyle{empty}

\definecolor{blueSky}{RGB}{49, 120, 198}

\begin{document}

% Header
\begin{flushleft}
\textbf{\Large Kenni Gandira Alamsyah}\\
Bangkok, Thailand\\
+66 0842704245\\
\href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com}\\
\href{https://www.linkedin.com/in/kenni-g-alamsyah}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{1em}

% Recipient
\begin{flushleft}
TikTok Hiring Team\\
Frontend Software Engineer - Growth\\
Singapore
\end{flushleft}

\vspace{1em}

Dear Hiring Manager,

\vspace{0.5em}

I am writing to express my interest in the Frontend Software Engineer - Growth role at TikTok. With 8 years of experience building frontend solutions and a track record of driving measurable user engagement improvements, I am excited to contribute to TikTok's growth initiatives.

\vspace{0.5em}

\textbf{Why I'm a strong fit for your Growth team:}

\vspace{0.3em}

Your focus on user acquisition and retention through data-driven approaches aligns with my experience. At PropertyScout, I contributed to a 27\% increase in Q3 user traffic through frontend optimizations. At AccelByte, I reduced compilation time by 40\%, improving team productivity. At 99.co, I helped reduce page load times from 4.5s to 1.2s, directly impacting user retention.

\vspace{0.5em}

\textbf{Technical alignment:}

\vspace{0.3em}

I bring strong proficiency in React, JavaScript, and modern frontend tools including Redux, Webpack, and Jest. I have extensive experience with testing frameworks and component documentation. While I haven't worked with Micro Frontends specifically, I've built modular, scalable applications and am eager to learn and apply new architectures.

\vspace{0.5em}

I'm drawn to TikTok's ``Always Day 1'' culture and the opportunity to work on growth experiments at scale. I would welcome the chance to discuss how my frontend expertise can help drive TikTok's continued growth.

\vspace{1em}

Best regards,

\vspace{0.5em}

Kenni Gandira Alamsyah

\end{document}