\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  bottom=25mm,
  top=25mm
}

\pagestyle{empty}

\definecolor{blueSky}{RGB}{49, 120, 198}

\begin{document}

% Header
\begin{flushleft}
\textbf{\Large Kenni Gandira Alamsyah}\\
Bangkok, Thailand\\
+66 0842704245\\
\href{mailto:devkenni.g@gmail.com}{devkenni.g@gmail.com}\\
\href{https://www.linkedin.com/in/kenni-g-alamsyah}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{1em}

% Recipient
\begin{flushleft}
TikTok Hiring Team\\
Frontend Software Engineer - Growth\\
Singapore
\end{flushleft}

\vspace{1em}

Dear Hiring Manager,

\vspace{0.5em}

I am writing to express my strong interest in the Frontend Software Engineer - Growth role at TikTok. With 8+ years of experience building scalable frontend solutions that drive user growth, I am excited to contribute to TikTok's mission of inspiring creativity and bringing joy to billions of users worldwide.

\vspace{0.5em}

\textbf{Why I'm passionate about TikTok's Growth team:}

\vspace{0.3em}

Your focus on leveraging data and ML models to power global growth aligns perfectly with my experience. At PropertyScout, I increased user traffic by 27\% through frontend optimizations. At AccelByte, I reduced compilation time by 40\%, significantly improving R\&D efficiency. At 99.co, my performance optimization work reducing LCP from 4.5s to 1.2s directly correlated with improved user retention metrics.

\vspace{0.5em}

\textbf{Technical expertise aligned with your needs:}

\vspace{0.3em}

I bring deep proficiency in React, JavaScript, and modern frontend architectures, with extensive experience in testing frameworks and build optimization. My approach to frontend development emphasizes both user experience and developer efficiency - creating solutions that delight users while enabling rapid iteration crucial for growth initiatives.

\vspace{0.5em}

I am inspired by TikTok's ``Always Day 1'' culture and the opportunity to work on growth experiments at unprecedented scale. I would be thrilled to discuss how my experience building performant, scalable frontend solutions can help TikTok continue its remarkable growth trajectory.

\vspace{1em}

Best regards,

\vspace{0.5em}

Kenni Gandira Alamsyah

\end{document}