\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  bottom=25mm,
  top=25mm
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Kenni Gandira Alamsyah}\\
Bangkok, Thailand\\
+66 0842704245\\
devkenni.g@gmail.com\\
\href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{1em}

\begin{flushleft}
Hiring Manager\\
Sundra\\
Remote
\end{flushleft}

\vspace{1em}

\textbf{RE: Lead Developer Position}

\vspace{1em}

Dear Sundra Hiring Team,

I'm energized by the Lead Developer opportunity at Sundra. Your AI-powered captioning tool represents exactly the kind of impactful work I'm passionate about—using technology to solve real accessibility challenges for teams worldwide.

Over 8+ years, I've architected scalable web applications delivering measurable results: 27\% traffic growth at PropertyScout, 40\% build performance improvement at AccelByte, and 73\% Core Web Vitals enhancement at 99.co. Your Vue/Nuxt/TypeScript stack aligns perfectly with my technical expertise, and I've successfully worked remotely with distributed teams across time zones.

What excites me most about Sundra is the opportunity to be a core engineering pillar—directly shaping product, culture, and technical strategy alongside your CTO and CEO. My PHP experience through CodeIgniter, combined with rapid learning ability, positions me to contribute across your full stack while leveraging my frontend strengths.

I thrive in startup environments where individual contributions create meaningful impact. Beyond delivering clean, scalable solutions, I drive engineering excellence through knowledge sharing, technical mentorship, and establishing standards that elevate entire teams.

I'm ready to help architect and scale Sundra's platform while growing with your team. Let's discuss how my proven track record and leadership mindset can accelerate Sundra's growth.

\vspace{1em}

Best regards,

\textbf{Kenni Gandira Alamsyah}

\end{document}
