\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  bottom=25mm,
  top=25mm
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Kenni Gandira Alamsyah}\\
Bangkok, Thailand\\
+66 0842704245\\
devkenni.g@gmail.com\\
\href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{1em}

\begin{flushleft}
Hiring Manager\\
Sundra\\
Remote
\end{flushleft}

\vspace{1em}

\textbf{RE: Lead Developer Position}

\vspace{1em}

Dear Sundra Hiring Team,

I'm excited about the Lead Developer opportunity at Sundra. Your AI-powered captioning tool represents the kind of meaningful work I'm passionate about—using technology to solve real accessibility challenges for teams worldwide.

Over 8+ years, I've built scalable web applications contributing to measurable results: 27\% traffic growth at PropertyScout, 40\% build performance improvement at AccelByte, and 73\% Core Web Vitals enhancement at 99.co. Your Vue/Nuxt/TypeScript stack aligns perfectly with my technical expertise, and I've worked effectively with distributed remote teams across time zones.

What excites me about Sundra is the opportunity to contribute as a core engineering member—working closely with your CTO and CEO to help shape product and technical direction. My PHP experience through CodeIgniter, combined with my eagerness to learn, positions me to contribute across your full stack while leveraging my frontend strengths.

I thrive in startup environments where individual contributions create meaningful impact. Beyond delivering clean, scalable solutions, I value knowledge sharing, technical mentorship, and helping establish standards that benefit entire teams.

I'm ready to help build and scale Sundra's platform while growing with your team. Let's discuss how my experience and collaborative approach can support Sundra's growth.

\vspace{1em}

Best regards,

\textbf{Kenni Gandira Alamsyah}

\end{document}
