\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  bottom=25mm,
  top=25mm
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Kenni Gandira Alamsyah}\\
Bangkok, Thailand\\
+66 0842704245\\
devkenni.g@gmail.com\\
\href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{1em}

\begin{flushleft}
Hiring Manager\\
Sundra\\
Remote
\end{flushleft}

\vspace{1em}

\textbf{RE: Lead Developer Position}

\vspace{1em}

Dear Sundra Hiring Team,

I'm excited to apply for the Lead Developer position at Sundra. Your AI-powered captioning and translation tool resonates deeply with me—accessibility through technology has been a consistent theme throughout my career, from optimizing Core Web Vitals for better user experiences to building tools that improve developer workflows.

What draws me to Sundra is the opportunity to architect and scale a platform using Vue/Nuxt and TypeScript—technologies I've worked with extensively across my 8+ years as a frontend engineer. At PropertyScout, I contributed to a 27\% traffic increase through systematic Vue.js application improvements. At AccelByte, I reduced compilation time by 40\% while working remotely with a distributed team. These experiences align perfectly with Sundra's remote-first culture and need for someone who can deliver clean, scalable solutions.

Your tech stack matches my strongest skills: Vue.js for component architecture, TypeScript for type-safe development, and TailwindCSS for rapid UI implementation. I've also worked with PHP through CodeIgniter projects and am eager to expand my Laravel expertise. Beyond the technical fit, I'm drawn to startups where individual contributions create meaningful impact. I thrive in collaborative environments where I can influence product direction while learning from talented teammates.

I'm particularly excited about working directly with your CTO and CEO to shape both the platform and company culture. My team-first approach, combined with experience building developer tools and component libraries, would allow me to contribute immediately while growing into the full-stack responsibilities this role offers.

Thank you for considering my application. I'd love to discuss how my Vue.js expertise, performance optimization background, and collaborative mindset can help Sundra scale its platform and achieve its mission.

\vspace{1em}

Best regards,

\textbf{Kenni Gandira Alamsyah}

\end{document}
