\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{
  a4paper,
  left=25mm,
  right=25mm,
  top=25mm,
  bottom=25mm
}

\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{\Large Kenni Gandira Alamsyah}\\[0.3em]
Bangkok, Thailand\\
+66 0842704245\\
devkenni.g@gmail.com\\
\href{https://www.linkedin.com/in/kenni-g-alamsyah/}{linkedin.com/in/kenni-g-alamsyah}
\end{flushleft}

\vspace{1.5em}

\noindent October 6, 2025

\vspace{1em}

\noindent Dear Hiring Manager,

\vspace{1em}

I am excited to apply for the Senior Web Developer position at KnitWell Group, where I can contribute to the digital experiences that empower women through AnnTaylor.com and LOFT.com. As a Frontend Engineer with 8+ years of eCommerce experience, I have a proven track record of delivering measurable business impact through technical excellence and collaboration.

\vspace{0.8em}

My achievements align directly with your Web Production team's priorities. At 99.co, I delivered performance optimization that reduced LCP from 4.5s to 1.2s (73\% improvement), while implementing comprehensive SEO strategies and schema validation that amplified site traffic. This experience translates directly to optimizing promotional content and campaign pages across your digital channels. At PropertyScout, I led technical execution of a web application revamp that delivered a 27\% increase in user traffic, demonstrating how strong technical execution drives tangible business results. These accomplishments earned me the ``Own It'' award for exceptional product ownership and recognition as part of the team that won the 99 Group Hackathon Best UI/UX Design award.

\vspace{0.8em}

I bring the precise technical expertise your team requires: advanced HTML, CSS, and JavaScript skills; experience with modern templating frameworks; proven performance, accessibility, and SEO optimization capabilities; and extensive CMS platform expertise with WordPress, Strapi, and OctoberCMS that transfers seamlessly to Salesforce Commerce Cloud. My track record includes W3C validation compliance, comprehensive cross-browser compatibility testing, and close collaboration with UX designers and marketing teams to transform creative visions into high-performing digital experiences.

\vspace{0.8em}

What excites me most about KnitWell Group is the opportunity to contribute to brands that make a genuine difference in women's lives while working in a culture that values empowerment and giving back. The hybrid model appeals to me---I thrive in collaborative environments where I can partner closely with producers, designers, and product managers to deliver polished customer experiences.

\vspace{0.8em}

I would welcome the opportunity to discuss how my performance optimization expertise, collaborative approach, and proven business impact can contribute to elevating the digital experiences for Ann Taylor and LOFT customers.

\vspace{0.8em}

Thank you for considering my application. I look forward to exploring this exciting opportunity with you.

\vspace{1.5em}

\noindent Best regards,

\vspace{0.5em}

\noindent Kenni Gandira Alamsyah

\end{document}
